---
title: "Nasville Music Venues Research"
author: "Sofia Fasullo"
date: "2023-03-21"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Start by loading in packages
```{r}
library(tidyverse)
library(sf)
#library(RSocrata)
library(tidycensus)
#library(tigris)
#library(viridis)
#library(viridisLite)
library(mapview)
library(dplyr)
#library(foreign)
#library(tidygeocoder)
```
Load venue datasets
```{r}
## load venue data (last updated: 08/09/2023)

venues = read.csv("~/Github/Nashville_IMV/data/venue_tables/New_8_9/venue_8_9_populated.csv") %>% 
  st_as_sf(coords = c("x","y"), 
           remove = FALSE, 
           crs= 4326, na.fail = FALSE) %>%
  group_by(name, address_admin, APN) %>%
  slice(1) %>%
  ungroup()

## venue APN data (last updated: 04/16/2023) - use this dataset as a "key" for all tabular joins
venue_admin_key_table = read.csv("~/GitHub/Nashville_IMV/data/venue_tables/simple_table_4_16.csv")

## data dictionary for detailed venue table
data_dictionary_load = read.csv("~/Github/Nashville_IMV/data/venue_tables/data_dictionary_venue_detailed_7_3.csv", header=F)
data_dictionary_view = t(data_dictionary_load) %>% as.data.frame() %>% mutate(col_name=V1,col_definition=V2,survey_question=V3) %>% select(-c(V1,V2,V3))
#view(data_dictionary_view)

```


NOTE: possiblility to streamline this system in the future by reading .R files into this markdown rather than having all this code re-written

#Joining Census Data to Parent Geography

- Use *~/Github/Nashville_IMV/R/clean_data.R* clean the music venue database so that it is in a format compatible to join with other data sets. 

- Then use the code below to inspect and visualize this information.

```{r}
## Sofia Fasullo's API key - replace with your own, get at https://api.census.gov/data/key_signup.html
API_key = "c03e04624fa724c446d835b3c313e3f11aa54c2d" 
census_api_key(API_key, overwrite = TRUE)

## Look through existing acs variables and choose a few to examine: filter geography to block group
acs_variable_list.2020 <- load_variables(2020,"acs5")
acs_variable_list.2010 <- load_variables(2010,"acs5")

## Set up lists of variables to grab
acs_vars_20 <- c("B01001_001E", # ACS total Pop estimate
              "B06011_001E", # Median income in past 12 months
              "B09021_008E", # 18-34 yr olds estimate
              "B25032_013E", # total renter-occupied units estimate
              "B25031_001E" # median rent estimate
              )

acs_vars_10 <- c("B01001_001E", # ACS total Pop estimate
              "B06011_001E", # Median income in past 12 months
              "B21005_002E", # 18-34 yr olds estimate
              "B25013_007E", # total renter-occupied units estimate
              "B25064_001E" # median rent estimate
              )

## Grab block-level for Davidson County: 2020 and 2010
acs2020 <- get_acs(geography = "tract",
                   year = 2020,
                   variables = (acs_vars_20),
                   geometry = TRUE,
                   state = "TN",
                   county = "Davidson",
                   output = "wide") %>%
  select(GEOID, NAME, acs_vars_20) %>%
  rename(total_pop_est = B01001_001E,
         median_income_est = B06011_001E,
         pop_18_34_est = B09021_008E,
         rental_units_est = B25032_013E,
         med_rent_est = B25031_001E) %>%
  mutate(year = 2020) %>% st_transform(4326)

acs2010 <- get_acs(geography = "tract",
                   year = 2010,
                   variables = all_of(acs_vars_10),
                   geometry = TRUE,
                   state = "TN",
                   county = "Davidson",
                   output = "wide") %>%
  select(GEOID, NAME, acs_vars_10) %>%
  rename(total_pop_est = B01001_001E,
         median_income_est = B06011_001E,
         pop_18_34_est = B21005_002E,
         rental_units_est = B25013_007E,
         med_rent_est = B25064_001E) %>%
  mutate(year = 2010) %>% st_transform(4326)

## combining tables in "long data" form - not used currently
#full_table <- rbind(acs2010, acs2020)
```

```{r}
## loading "parent" geography: city council districts (the match up to census block boundaries and )
#council_districts = st_read("https://data.nashville.gov/resource/iw7r-m8qr.geojson") %>% select(council_district, geometry) %>% st_transform(crs=4326)
planning_districts = st_read("~/Github/Nashville_IMV/data/metro/Subareas/Subareas/Subareas.shp") %>% 
  st_transform(crs=4326)
planning_districts$area = st_area(planning_districts)
```

Idea is 2 different "big" tables: one organized by census tract and one organized by venue (for ease of different access)

```{r}
## create new table of census acs data to manipulate
census10 = acs2010
census10[is.na(census10)] <- 0 #allow for calculations to be made

## calculate new columns (in this case, area, population density, and preparation to calculate average median income)
census10$area10 = st_area(census10) # this is in sq meters
census10 = census10 %>% mutate(pop_dens10 = total_pop_est/area10, med_incxpop = median_income_est*total_pop_est, perc_youth = round((pop_18_34_est/total_pop_est)*100,1), med_rentxpop = med_rent_est*total_pop_est)

## join blocks to council districts and aggregate block data by council districts
plan10 = st_join(planning_districts,census10) %>% group_by(Communit_1) %>% summarize(tot_pop10 = sum(total_pop_est), avg_med_inc10 = (sum(med_incxpop)/tot_pop10), avg_dens10 = mean(pop_dens10), tot_youth10 = sum(pop_18_34_est), perc_youth_10 = mean(perc_youth), avg_med_rent10 = (sum(med_rentxpop)/tot_pop10), tot_rent_HH_10 = sum(rental_units_est))

## repeat process with 2020 data
census20 = acs2020
census20[is.na(census20)] <- 0
census20$area20 = st_area(census20)
census20 = census20 %>% mutate(pop_dens20 = total_pop_est/area20, med_incxpop = median_income_est*total_pop_est, perc_youth = round((pop_18_34_est/total_pop_est)*100,1), med_rentxpop = med_rent_est*total_pop_est)
plan20 = st_join(planning_districts,census20) %>% group_by(Communit_1) %>% summarize(tot_pop20 = sum(total_pop_est), avg_med_inc20 = (sum(med_incxpop)/tot_pop20), avg_dens20 = mean(pop_dens20), tot_youth20 = sum(pop_18_34_est), perc_youth_20 = mean(perc_youth), avg_med_rent20 = (sum(med_rentxpop)/tot_pop20), tot_rent_HH_20 = sum(rental_units_est))

## create dataset with council districts containing aggregated census data from both years AND further calculated columns (percent change population, percent change average median income, percent change in population density)
plan_dist = 
  left_join(st_drop_geometry(plan10), st_drop_geometry(plan20), by="Communit_1") %>%
  left_join(.,planning_districts,by="Communit_1") %>%
  st_as_sf() %>% 
  mutate(perc_chg_pop = round(((tot_pop20-tot_pop10)/tot_pop10)*100,1), perc_chg_med_inc = round(((avg_med_inc20-avg_med_inc10)/avg_med_inc10)*100,1), perc_chg_dens = round(((avg_dens20-avg_dens10)/avg_dens10)*100,1), perc_chg_med_rent = round(((avg_med_rent20-avg_med_rent10)/avg_med_rent10)*100,1), perc_chg_youth = round(((perc_youth_20-perc_youth_10)/perc_youth_10)*100,1))
```




```{r}
## creating table of venues with census acs data (aggregated by council districts) added on
#venues_dist = st_join(venues,coun_dist)

venues_dist = st_join(venues, plan_dist %>%
                        select(Communit_1))

```

## Making Sense of Administrative Data

- Use *~/Github/Nashville_IMV/R/clean_data.R* clean the music venue database so that it is in a format compatible to join with other data sets. 

- Then use the code below to inspect and visualize this information.

Fire department dataset cleaning
```{r}
## load fire department data
FD = st_read("~/Github/Nashville_IMV/data/metro/Bars-&-Nightclubs-with-Occupant-Loads_2023-03-24_131105.csv")

#94 venues match, 198 venues of ours not represented inn FD, 162 FD not represented in venues
venue_all_FD_data = left_join(venue_admin_key_table,FD,by= c("address_admin"="Location.Name","APN"="Location.Property.Tax.ID")) %>% unique()

#variables_FD = c() #feel like all of them are useful

#venue_select_parcel_data = venue_all_parcel_data %>% select(all_of(variables_parcels)) 

## FD data we want
addresses_to_pull = venue_all_FD_data %>% filter(is.na(Location.Full.Address)) %>% select(name,APN,address_admin)
```


Parcels dataset cleaning

MF - the issue here is that you are dropping leading zeros - fixed that with the str_pad
```{r}
## load administrative data (very time consuming)
parcels = st_read("~/Github/Nashville_IMV/data/metro/Nashville_Parcel_data.shp") %>% st_transform(4326)

venue_all_parcel_data = left_join(venue_admin_key_table %>%
                                    mutate(APN = str_pad(APN, width = 11, side = "left", pad = "0")), 
                                  parcels,
                                  by= c("address_admin"="PropAddr",
                                        "APN" = "APN")) %>% 
  unique()

variables_parcels = c("name", "address_admin", "APN", "TotlAppr", 
                      "LandAppr", "ImprAppr", "OwnDate", "AssessDate",
                      "TotlAssd", "LandAssd", "ImprAssd",
                      "SalePrice", "Acres", "FinishArea", "LUDesc", 
                      "Owner", "OwnAddr1", "OwnAddr2", "OwnCity",
                      "OwnState", "OwnZip", "Council", "geometry")

venue_select_parcel_data = venue_all_parcel_data %>% 
  select(all_of(variables_parcels)) %>% 
  mutate(Area_sqft = Acres*43560)

venue_full = left_join(venue_select_parcel_data, venues_dist %>%
                         as.data.frame() %>% 
                         mutate(APN = str_pad(APN, width = 11, side = "left", pad = "0")) %>%
                         select(-geometry), by = c("address_admin", "APN", "name")) %>%
  mutate(x=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         y=map_dbl(geometry, ~st_centroid(.x)[[2]]))
#area is of parcel not building so I will not calculate price/sqft just yet
#will get centroids from venues table rather than re-calculating
```

## Aggregating to district

- aggregate w/mean: interdisciplinary through experimentation do mean (except purpose), capacity
- aggregate w/sum: num_venues, independent_booking, ownership (together and separate), capacity

MF - we will make changes to the aggregation process if we see things in the venue data that we want to summarize
For example we might want to do something here that summarizes things by frequent/infrequent venues etc.,
We still have some issues here with NaN values in the census info. Not a big deal if we have NA values for areas with 1 venue

```{r}
## aggregating venue data by council district area and creating table of council districts with census acs and venue data

d1_aggregates = st_join(plan_dist, venue_full %>%
                                      as.data.frame() %>%
                                      st_as_sf(coords = c("x", "y"), crs = 4326) %>%
                                      mutate(independent_booking_and_ownership = 
                                               ifelse(independent_booking_ord == 1 & 
                                                        ownership_structure_ord == 1, 1,0),
                                              quasi_independent = 
                                               ifelse(independent_booking == "2. Sometimes" &
                                                        ownership_structure_ord == 1, 1, 0)) %>%
                                      select(capacity,
                                             ownership_structure_ord,
                                             independent_booking_ord,
                                             independent_booking_and_ownership,
                                             interdisciplinarity_ord,
                                             quasi_independent,
                                             event_promotion_ord,
                                             community_focus_ord,
                                             creativity_ord,
                                             experimentation_ord)) %>% 
#not sure why NAs are introduced  
  group_by(Communit_1) %>% 
  summarize(num_venues = n(),
            avg_capacity = mean(as.numeric(capacity),na.rm=TRUE),
            median_capacity = median(as.numeric(capacity), na.rm = TRUE),
            total_capacity = sum(as.numeric(capacity), na.rm = TRUE),
            independent_ownership = sum(ownership_structure_ord,na.rm=TRUE),
            independent_booking = sum(independent_booking_ord,na.rm=TRUE),
            independent_booking_and_ownership = sum(independent_booking_and_ownership,na.rm=TRUE),
            quasi_independent = sum(quasi_independent, na.rm = TRUE),
            interdisciplinarity = mean(interdisciplinarity_ord,na.rm=TRUE),
            event_promotion = mean(event_promotion_ord,na.rm=TRUE),
            community_focus = mean(community_focus_ord,na.rm=TRUE),
            creativity = mean(creativity_ord,na.rm=TRUE),
            experimentation = mean(experimentation_ord,na.rm=TRUE),
            ) %>% 
  left_join(., st_drop_geometry(plan_dist), by="Communit_1") %>% 
  mutate(density_venues = num_venues/area)

```

Business Licenses Dataset cleaning
```{r}
business_licenses = read.csv("~/Github/Nashville_IMV/data/metro/Business_Property.csv")

venue_all_business_data = left_join(venue_admin_key_table,business_licenses,by="APN")

variables_business = c("name","BUSNAME","address_admin","PropAddr","APN","BUSTYPE","OWNER","APPRVALUE","ASSDVALUE")

venue_select_business_data = select(venue_all_business_data,all_of(variables_business))
```

## Write out the data

```{r}

st_write(d1_aggregates, "~/GitHub/Nashville_IMV/data/venue_tables/to_map/d1_aggregate_v2.geojson")

st_write(venue_full, "~/GitHub/Nashville_IMV/data/venue_tables/to_map/venues_v2.geojson")

```
