---
title: "Nasville Music Venues Research"
author: "Sofia Fasullo & Michael Fichman"
date: "2024-2-16"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    code_folding: hide
---

Data Routine to join cleaned venue data to municipal data, and  and aggregate/summarize by neighborhood units

Last update - Feb 16, 2024

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Start by loading in packages
```{r}
library(tidyverse)
library(sf)
#library(RSocrata)
library(tidycensus)
#library(tigris)
#library(viridis)
#library(viridisLite)
library(mapview)
library(dplyr)
#library(foreign)
#library(tidygeocoder)
```
Load venue datasets
```{r}
## load venue data (last updated: 08/09/2023)

venues = read.csv("~/Github/Nashville_IMV/data/venue_tables/new_8_24/venue_table_8_24_populated.csv") %>% 
  st_as_sf(coords = c("x","y"), 
           remove = FALSE, 
           crs= 4326, na.fail = FALSE) %>%
  group_by(name) %>%
  slice(1) %>%
  ungroup()

## venue APN data (last updated: 04/16/2023) - use this dataset as a "key" for all tabular joins
venue_admin_key_table = read.csv("~/GitHub/Nashville_IMV/data/venue_tables/simple_table_4_16.csv")

## data dictionary for detailed venue table
data_dictionary_load = read.csv("~/Github/Nashville_IMV/data/venue_tables/data_dictionary_venue_detailed_7_3.csv", header=F)
data_dictionary_view = t(data_dictionary_load) %>% as.data.frame() %>% mutate(col_name=V1,col_definition=V2,survey_question=V3) %>% select(-c(V1,V2,V3))
#view(data_dictionary_view)

```


NOTE: possiblility to streamline this system in the future by reading .R files into this markdown rather than having all this code re-written

Make a few quick data substitutions to reflect some changes in data set.

Includes changes on 2/16 for final report edit - changing city winery ownership structure to non-independent, removing Hi Watt (was not open at survey time)

```{r}

venues <- venues %>%
  mutate(independent_booking = ifelse(name == "3rd & Lindsley", "3. Never", independent_booking),
         events_per_month = ifelse(name == "Nissan Stadium", "1. 1-4 Events per month", events_per_month),
         ownership_structure = ifelse(name == "City Winery", "2. No", ownership_structure)) %>%
  filter(str_detect(name, "High Watt") == FALSE)

```

#Joining Census Data to Parent Geography

- Use *~/Github/Nashville_IMV/R/clean_data.R* clean the music venue database so that it is in a format compatible to join with other data sets. 

- Then use the code below to inspect and visualize this information.

```{r}
## Sofia Fasullo's API key - replace with your own, get at https://api.census.gov/data/key_signup.html
API_key = "c03e04624fa724c446d835b3c313e3f11aa54c2d" 
census_api_key(API_key, overwrite = TRUE)

## Look through existing acs variables and choose a few to examine: filter geography to block group
acs_variable_list.2020 <- load_variables(2020,"acs5")
acs_variable_list.2010 <- load_variables(2010,"acs5")

## Set up lists of variables to grab
acs_vars_20 <- c("B01001_001E", # ACS total Pop estimate
              "B06011_001E", # Median income in past 12 months
              "B09021_008E", # 18-34 yr olds estimate
              "B25032_013E", # total renter-occupied units estimate
              "B25031_001E" # median rent estimate
              )

acs_vars_10 <- c("B01001_001E", # ACS total Pop estimate
              "B06011_001E", # Median income in past 12 months
              "B21005_002E", # 18-34 yr olds estimate
              "B25013_007E", # total renter-occupied units estimate
              "B25064_001E" # median rent estimate
              )

## Grab block-level for Davidson County: 2020 and 2010
acs2020 <- get_acs(geography = "tract",
                   year = 2020,
                   variables = (acs_vars_20),
                   geometry = TRUE,
                   state = "TN",
                   county = "Davidson",
                   output = "wide") %>%
  select(GEOID, NAME, acs_vars_20) %>%
  rename(total_pop_est = B01001_001E,
         median_income_est = B06011_001E,
         pop_18_34_est = B09021_008E,
         rental_units_est = B25032_013E,
         med_rent_est = B25031_001E) %>%
  mutate(year = 2020) %>% st_transform(4326)

acs2010 <- get_acs(geography = "tract",
                   year = 2010,
                   variables = all_of(acs_vars_10),
                   geometry = TRUE,
                   state = "TN",
                   county = "Davidson",
                   output = "wide") %>%
  select(GEOID, NAME, acs_vars_10) %>%
  rename(total_pop_est = B01001_001E,
         median_income_est = B06011_001E,
         pop_18_34_est = B21005_002E,
         rental_units_est = B25013_007E,
         med_rent_est = B25064_001E) %>%
  mutate(year = 2010) %>% st_transform(4326)

## combining tables in "long data" form - not used currently
#full_table <- rbind(acs2010, acs2020)
```

```{r}
## loading "parent" geography: city council districts (the match up to census block boundaries and )
#council_districts = st_read("https://data.nashville.gov/resource/iw7r-m8qr.geojson") %>% select(council_district, geometry) %>% st_transform(crs=4326)
planning_districts = st_read("~/Github/Nashville_IMV/data/metro/Subareas/Subareas/Subareas.shp") %>% 
  st_transform(crs=4326)
planning_districts$area = st_area(planning_districts)
```

Idea is 2 different "big" tables: one organized by census tract and one organized by venue (for ease of different access)

```{r}
## create new table of census acs data to manipulate
census10 = acs2010
census10[is.na(census10)] <- 0 #allow for calculations to be made

## calculate new columns (in this case, area, population density, and preparation to calculate average median income)
census10$area10 = st_area(census10) # this is in sq meters
census10 = census10 %>% mutate(pop_dens10 = total_pop_est/area10, 
                               med_incxpop = median_income_est*total_pop_est, 
                               perc_youth = round((pop_18_34_est/total_pop_est)*100,1), 
                               med_rentxpop = med_rent_est*total_pop_est)

## join blocks to council districts and aggregate block data by council districts
plan10 = st_join(planning_districts, census10 %>%
                   st_centroid()) %>% 
  group_by(Communit_1) %>%
  summarize(tot_pop10 = sum(total_pop_est), 
            avg_med_inc10 = (sum(med_incxpop)/tot_pop10), 
            avg_dens10 = mean(pop_dens10), 
            tot_youth10 = sum(pop_18_34_est), 
            perc_youth_10 = mean(perc_youth), 
            avg_med_rent10 = (sum(med_rentxpop)/tot_pop10), 
            tot_rent_HH_10 = sum(rental_units_est))

## repeat process with 2020 data
census20 = acs2020
census20[is.na(census20)] <- 0
census20$area20 = st_area(census20)
census20 = census20 %>% 
  mutate(pop_dens20 = total_pop_est/area20, 
         med_incxpop = median_income_est*total_pop_est, 
         perc_youth = round((pop_18_34_est/total_pop_est)*100,1), 
         med_rentxpop = med_rent_est*total_pop_est)

plan20 = st_join(planning_districts, census20 %>%
                   st_centroid()) %>% 
  group_by(Communit_1) %>% 
  summarize(tot_pop20 = sum(total_pop_est), 
            avg_med_inc20 = (sum(med_incxpop)/tot_pop20), 
            avg_dens20 = mean(pop_dens20), 
            tot_youth20 = sum(pop_18_34_est), 
            perc_youth_20 = mean(perc_youth), 
            avg_med_rent20 = (sum(med_rentxpop)/tot_pop20), 
            tot_rent_HH_20 = sum(rental_units_est))

## create dataset with council districts containing aggregated census data from both years AND further calculated columns (percent change population, percent change average median income, percent change in population density)
plan_dist = 
  left_join(st_drop_geometry(plan10), st_drop_geometry(plan20), by="Communit_1") %>%
  left_join(.,planning_districts,by="Communit_1") %>%
  st_as_sf() %>% 
  mutate(perc_chg_pop = round(((tot_pop20-tot_pop10)/tot_pop10)*100,1), 
         perc_chg_med_inc = round(((avg_med_inc20-avg_med_inc10)/avg_med_inc10)*100,1), 
         perc_chg_dens = round(((avg_dens20-avg_dens10)/avg_dens10)*100,1), 
         perc_chg_med_rent = round(((avg_med_rent20-avg_med_rent10)/avg_med_rent10)*100,1), 
         perc_chg_youth = round(((perc_youth_20-perc_youth_10)/perc_youth_10)*100,1))
```




```{r}
## creating table of venues with census acs data (aggregated by council districts) added on
#venues_dist = st_join(venues,coun_dist)

venues_dist = st_join(venues, plan_dist %>%
                        select(Communit_1))

```

## Making Sense of Administrative Data

- Use *~/Github/Nashville_IMV/R/clean_data.R* clean the music venue database so that it is in a format compatible to join with other data sets. 

- Then use the code below to inspect and visualize this information.

Fire department dataset cleaning

MF - just updated this on 10/6 for new data
```{r }
## load fire department data
FD = read.csv("~/Github/Nashville_IMV/data/metro/fire_dept_oct_6_capacities.csv") %>%
  mutate(Occ.Load = ifelse(Occ.Load == "283 (2 bldgs)", "283", Occ.Load),
         Occ.Load = as.numeric(Occ.Load))

# Join the fire data by address_admin and name
# Coerce Chamber data to numeric
# Choose whichever capacity value is larger (the smaller values tend to look very wrong) in a column called Capacity
# Rename the chamber capacity as "chamber_capacity", fire capacity as "fd_capacity"
# Make a note which capacity we are using in a new colum called "capacity_source"
venues_dist = left_join(venues_dist %>%
                   mutate(capacity = ifelse(capacity %in% c("Null", ""), NA, capacity),
                          capacity = as.numeric(gsub(",", "", capacity))), FD %>%
                   select(address_admin, name, Occ.Load)) %>% 
  rename(chamber_capacity = capacity,
         fd_capacity = Occ.Load) %>%
  mutate(Capacity = case_when(chamber_capacity >= fd_capacity ~ chamber_capacity,
                              fd_capacity > chamber_capacity ~ fd_capacity,
                              is.na(chamber_capacity) == TRUE & is.na(fd_capacity) == FALSE ~ fd_capacity,
                              is.na(chamber_capacity) == FALSE & is.na(fd_capacity) == TRUE ~ chamber_capacity),
         Capacity_source = case_when(chamber_capacity == Capacity ~ "Nash. Area Chamber of Commerce",
                                     fd_capacity == Capacity ~ "Metro Nashville Fire Department",
                                     is.na(Capacity) == TRUE ~ "No Data Available"))

#variables_FD = c() #feel like all of them are useful

#venue_select_parcel_data = venue_all_parcel_data %>% select(all_of(variables_parcels)) 

## FD data we want
#addresses_to_pull = venue_all_FD_data %>% filter(is.na(Location.Full.Address)) %>% select(name,APN,address_admin)
```


Parcels dataset cleaning

MF - the issue here is that you are dropping leading zeros - fixed that with the str_pad
```{r}
## load administrative data (very time consuming)
parcels = st_read("~/Github/Nashville_IMV/data/metro/Nashville_Parcel_data.shp") %>% st_transform(4326)

venue_all_parcel_data = left_join(venues_dist %>%
                                    as.data.frame() %>%
                                    select(-geometry) %>%
                                    mutate(APN = str_pad(APN, width = 11, side = "left", pad = "0")), 
                                  parcels,
                                  by= c("address_admin"="PropAddr",
                                        "APN" = "APN")) %>% 
  unique()

variables_parcels = c("name", "address_admin", "APN", "TotlAppr", 
                      "LandAppr", "ImprAppr", "OwnDate", "AssessDate",
                      "TotlAssd", "LandAssd", "ImprAssd", "ParID",
                      "SalePrice", "Acres", "FinishArea", "LUDesc", 
                      "Owner", "OwnAddr1", "OwnAddr2", "OwnCity",
                      "OwnState", "OwnZip", "Council", "geometry")

venue_select_parcel_data = venue_all_parcel_data %>% 
  select(all_of(variables_parcels)) %>% 
  mutate(Area_sqft = Acres*43560)

venue_full = left_join(venue_select_parcel_data, venues_dist %>%
                         as.data.frame() %>% 
                         mutate(APN = str_pad(APN, width = 11, side = "left", pad = "0")) %>%
                         select(-geometry), by = c("address_admin", "APN", "name")) %>%
  mutate(x=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         y=map_dbl(geometry, ~st_centroid(.x)[[2]]))
#area is of parcel not building so I will not calculate price/sqft just yet
#will get centroids from venues table rather than re-calculating
```



```{r}
# Save an object that's just venue info and polygons

venue_polygons <- venue_full %>%
  st_as_sf() %>%
  select(name, address_admin, APN)

```

## Zoning data

The zoning data have a lot of busted vertices - 19 features with invalid spherical geometry

```{r}
zoning <- st_read("~/Github/Nashville_IMV/data/metro/Zoning/Zoning/Zoning_polygons.shp") %>% st_transform(4326)

```
Analyze a bit about the zoning in general (considering moving this into the markdown)

```{r}
zoning %>%
  st_make_valid() %>%
  mutate(area_kmsq = as.numeric(st_area(.) / 1000)) %>%
  as.data.frame() %>%
  group_by(ZONE_DESC) %>%
  summarize(tot_area_kmsq = sum(area_kmsq)) %>%
  arrange(-tot_area_kmsq)

```


```{r}
venue_full <- st_join(venue_full %>%
                  as.data.frame() %>%
                  st_as_sf(coords = c("x", "y"), crs = 4326), zoning %>%
                  st_make_valid() %>%
                    select(ZONE_DESC, ZONE_TYPE, NAME, ORDINANCE) %>%
                    rename(ZONE_NAME = NAME,
                           ZONE_ORDINANCE = ORDINANCE))

```

## Add IMV indicators

```{r}
venue_full <- venue_full %>%
  mutate(music_space = ifelse(purpose %in% c("3. Somewhat likely", 
                                             "4. Very Likely") &
                                events_per_month %in% c("2. 5-10 Events per month",
                                                        "3. 11-20 Events per month",
                                                        "4. 20+ Events per month"),
                              "Music Space", "Occasional Music Space")) %>%
  mutate(IMV = case_when(ownership_structure == "1. Yes" & independent_booking == "3. Never" ~
                           "Indep. Owned and Operated",
                         ownership_structure == "1. Yes" & independent_booking == "2. Sometimes" ~
                           "Quasi-independent",
                         ownership_structure == "1. Yes" & independent_booking == "4. Information unavailable" ~
                           "Quasi-independent"))%>%
  mutate(IMV = ifelse(is.na(IMV) == TRUE, "Non-Independent", IMV))

```

## Aggregating to district

- aggregate w/mean: interdisciplinary through experimentation do mean (except purpose), capacity
- aggregate w/sum: num_venues, independent_booking, ownership (together and separate), capacity

MF - we will make changes to the aggregation process if we see things in the venue data that we want to summarize
For example we might want to do something here that summarizes things by frequent/infrequent venues etc.,
We still have some issues here with NaN values in the census info. Not a big deal if we have NA values for areas with 1 venue

```{r}
## aggregating venue data by council district area and creating table of council districts with census acs and venue data

d1_aggregates = st_join(plan_dist, venue_full %>%
                                      mutate(music_space_ord = 
                                               ifelse(music_space == "Music Space", 1,0),
                                              IMV_ord = 
                                               ifelse(music_space == "Music Space" &
                                                        IMV == "Indep. Owned and Operated", 1, 0),
                                             Quasi_IMV_ord = 
                                               ifelse(music_space == "Music Space" &
                                                        IMV == "Quasi-independent", 1, 0),
                                             Non_IMV_ord = 
                                               ifelse(music_space == "Music Space" &
                                                        IMV == "Non-Independent", 1, 0)) %>%
                                      select(Capacity,
                                             music_space_ord,
                                             IMV_ord,
                                             Quasi_IMV_ord,
                                             Non_IMV_ord,
                                             interdisciplinarity_ord,
                                             event_promotion_ord,
                                             community_focus_ord,
                                             experimentation_ord)) %>% 
#not sure why NAs are introduced  
  group_by(Communit_1) %>% 
  summarize(num_venues = n(),
            num_music_smaces = sum(music_space_ord, na.rm = TRUE),
            avg_capacity = mean(as.numeric(Capacity),na.rm=TRUE),
            median_capacity = median(as.numeric(Capacity), na.rm = TRUE),
            total_capacity = sum(as.numeric(Capacity), na.rm = TRUE),
            IMV_n = sum(IMV_ord,na.rm=TRUE),
            Quasi_IMV_n = sum(Quasi_IMV_ord,na.rm=TRUE),
            Non_IMV_n = sum(Non_IMV_ord,na.rm=TRUE),
            interdisciplinarity = mean(interdisciplinarity_ord,na.rm=TRUE),
            event_promotion = mean(event_promotion_ord,na.rm=TRUE),
            community_focus = mean(community_focus_ord,na.rm=TRUE),
            experimentation = mean(experimentation_ord,na.rm=TRUE)) %>% 
  left_join(., st_drop_geometry(plan_dist), by="Communit_1") %>% 
  mutate(density_venues = num_venues/area)

```

## Building Conditions database

Load building conditions shp, join to venue_full by parcel ID

```{r}

conditions <- st_read("~/Github/Nashville_IMV/data/metro/Build/Build/Build/Prop_Polys_with_Build_Characteristics.shp") %>% st_transform(4326)

venue_full <- left_join(venue_full, conditions %>% 
                    as.data.frame() %>% 
                    select(Condition, YearBuilt, APN, ParcelID), 
                  by = c("ParID" = "ParcelID", "APN" = "APN")) %>%
  group_by(name) %>%
  slice(1) %>%
  ungroup()
```


## Business Licenses Dataset cleaning


```{r}
#Whole database

business_licenses = read.csv("~/Github/Nashville_IMV/data/metro/Business_Property.csv")

# Sofia cleaned database

manual_business_match = read.csv("~/Github/Nashville_IMV/data/metro/manual_business_license.csv")
#1321 to 469 but still need to get to 279
#hotel - hotel or restaurant
# some confusing
# live manager
# some have nothing
# there are duplicates

 
```

Join the business records to the main venue data set.

```{r}
venue_full <- left_join(venue_full, manual_business_match %>%
                         as.data.frame() %>% 
                    select(-X) %>%
                    rename(BIZ_OWNER = OWNER,
                           BIZ_ACCOUNT = ACCOUNT,
                           BIZ_APPRVALUE = APPRVALUE,
                           BIZ_ASSD_VALUE = ASSDVALUE) %>%
                         mutate(APN = str_pad(APN, width = 11, side = "left", pad = "0")),
                  by = c("address_admin", "APN", "name")) %>%
  group_by(name) %>%
  slice(1)


```

Correct a few alias issues in the property data, and create an indicator called site_control that indicates if the property owner lists the business address as its location.

```{r}

venue_full <- venue_full %>%
  mutate(OwnAddr1 = ifelse(name == "The Basement", "1604 8TH AVE S", OwnAddr1),
         OwnAddr1 = ifelse(name == "Alley Taps", "162 4TH AVE N 205", OwnAddr1),
         OwnAddr1 = ifelse(name == "The Big Bang Dueling Pianos", "209 3RD AVE N", OwnAddr1),
         OwnAddr1 = ifelse(name == "Rocketown (Main Building)", "601 4TH AVE S", OwnAddr1),
         OwnAddr1 = ifelse(name == "Robert's Western World", "416 B BROADWAY", OwnAddr1)) %>%
  mutate(site_control = ifelse(OwnAddr1 == PropAddr |
                               OwnAddr1 == address_admin, "On-Site Owner Address", "Off-Site Owner Address")) 

```

## Clean venue data before writing out

```{r}
venue_full <- venue_full %>%
  select(-genre, -matches("venueType")) %>%
  mutate(x=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         y=map_dbl(geometry, ~st_centroid(.x)[[2]])) %>%
  as.data.frame() %>%
  select(-geometry) %>%
  left_join(venue_polygons, ., 
            by = c("address_admin", "APN", "name"))


```

## Write out the data

```{r}

st_write(d1_aggregates, "~/GitHub/Nashville_IMV/data/venue_tables/to_map/d1_aggregate_v9.geojson")

st_write(venue_full, "~/GitHub/Nashville_IMV/data/venue_tables/to_map/venues_v8.geojson")

```



```

