---
title: "Nashville Venues Project Data Portal"
author: "Michael Fichman & Sofia Fasullo for PennPraxis"
date: "7/14/2023"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: cosmo
    code_folding: hide
    code_download: no
  pdf_document:
    toc: yes
---


NOTES AND TO-DO's:

- Run this with real Nashville d1 aggregates
- Need to deal more in percentages - overall numbers of IMV vs non-IMV make graphic comparisons tough

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# ---- Load Packages ----
#list of packages


library(tidyverse)
library(data.table)
library(sf)
library(viridis)
library(viridisLite)
#library(translateR)
library(kableExtra)
library(leaflet)
library(leaflet.extras)
library(lubridate)
library(mapview)
library(DT)

# ---- Load Graphic Palettes ----

# Load a ggplot theme and a color palette

plotTheme <- theme(
  plot.title =element_text(size=12),
  plot.subtitle = element_text(size=8),
  plot.caption = element_text(size = 6),
  axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
  axis.text.y = element_text(size = 10),
  axis.title.y = element_text(size = 10),
  # Set the entire chart region to blank
  panel.background=element_blank(),
  plot.background=element_blank(),
  #panel.border=element_rect(colour="#F0F0F0"),
  # Format the grid
  panel.grid.major=element_line(colour="#D0D0D0",size=.75),
  axis.ticks=element_blank())

mapTheme <- theme(plot.title =element_text(size=12),
                  plot.subtitle = element_text(size=8),
                  plot.caption = element_text(size = 6),
                  axis.line=element_blank(),
                  axis.text.x=element_blank(),
                  axis.text.y=element_blank(),
                  axis.ticks=element_blank(),
                  axis.title.x=element_blank(),
                  axis.title.y=element_blank(),
                  panel.background=element_blank(),
                  panel.border=element_blank(),
                  panel.grid.major=element_line(colour = 'transparent'),
                  panel.grid.minor=element_blank(),
                  legend.direction = "vertical", 
                  legend.position = "right",
                  plot.margin = margin(1, 1, 1, 1, 'cm'),
                  legend.key.height = unit(1, "cm"), legend.key.width = unit(0.2, "cm"))

palette <- c("#10142A", "#47E9B9", "#F55D60", "#71EA48", "#C148EA", "#EAC148")
viridisPalette <- c("#440154", "#73D055", "#F55D60", "#238A8D", "#FDE725")
CityPalette <- c("#A230C2", "#3AEAB8", "#F9C700", "#0069FC", "#EF3340", "#bdbdbd") # Berlin, NYC, Tokyo, Stockholm, Montreal, Sydney
```

```{r load_cfp_data, message=FALSE, warning=FALSE, results = 'hide'}

# LOAD IN THE CFP DATA FOR COMPARISONS

# Read in district aggregates
d1_aggregates <- st_read("~/GitHub/CFP/unified__city_data/district_aggregates/d1_aggregates_11_16_22.geojson") %>%
  st_as_sf(crs = 4326)

d2_aggregates <- st_read("~/GitHub/CFP/unified__city_data/district_aggregates/d2_aggregates_06_15_23.geojson") %>%
  st_as_sf(crs = 4326) %>%
  rename(d2_name = d2_name.x)


# Read in venues
main_venue_data <- read.csv("~/GitHub/CFP/unified__city_data/main_venue_data_final_testSydney.csv") %>%
  mutate(city = ifelse(city == "Solna", "Stockholm", city))

# Read in EPSG information

source("~/GitHub/CFP/unified__city_data/epsg_list.R")


```

```{r load_nash_data, message=FALSE, warning=FALSE, results = 'hide'}

# LOAD IN THE NASH DATA

# Read in district aggregates
d1_aggregates_nash <- st_read("~/GitHub/Nashville_IMV/data/venue_tables/to_map/d1_aggregate.geojson") %>%
  st_as_sf(crs = 4326) %>%
  rename(venue_count = num_venues,
         d1_name = Communit_1)

d2_aggregates_nash <- st_read("~/GitHub/CFP/unified__city_data/district_aggregates/d2_aggregates_06_15_23.geojson") %>%
  st_as_sf(crs = 4326) %>%
  rename(d2_name = d2_name.x)


# Read in venues - THIS IS THE FILEPATH IN Data_Markdown.Rmd as of 7/18/2023
nash_venue_data <- st_read("~/GitHub/Nashville_IMV/data/venue_tables/to_map/venues.geojson") %>%
  st_transform(crs = 4326) %>%
  group_by(name) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(x=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         y=map_dbl(geometry, ~st_centroid(.x)[[2]])) %>%
  mutate(X = row_number()) %>%
  as.data.frame()


```

```{r create_basemaps}
library(ggmap)


ll <- function(dat, proj4 = 4326){
st_transform(dat, proj4)
}
```

```{r message = FALSE}
base_map1 <-get_stamenmap(bbox = unname(st_bbox(ll(st_buffer(st_centroid(d1_aggregates_nash),10000)))),
                    force = TRUE, maptype = "toner-lite", zoom = 11)

```

# 1. Key Takeaways



# 2. Data Sources

- IMV data set

- Chamber of Commerce Data (link)

- US Census

- Nashville Metro Cadastral

- Nashville Metro Parcels

- Nashville Metro Fire Inspection Data

- Nashville Planning Districts

# 3. Methods

What did we do?

We collected the data set with liaisons, community members and desk research (this will be covered by VL in the report)

We related each venue to it's APN number (a property identifier) and joined it to tax records, license records.

We created variables for knn sq ft costs, dist to CBD centroid, joined venues to districts

# 4. Venue Database

Let's give descriptive statistics for the venue database

Searchable database

```{r}
datatable(nash_venue_data, 
          options = list(pageLength = 10))
```

## 4.1. Total number of venues

- How many venues

```{r}
nrow(nash_venue_data)

```

### 4.1.2. Number of IMVs


## 4.2. Venue locations

- Where are they located? - Point map, Symbologized by planning area. 

NOTE - we should symbologize IMV status in these

### 4.2.1. Interactive Map 

```{r leaflet, message= FALSE, warning=FALSE}

l <- leaflet() %>% 
  addProviderTiles(providers$Esri.WorldTopoMap) %>%
  setView(lng = mean(nash_venue_data$x, na.rm = TRUE),
          lat = mean(nash_venue_data$y, na.rm = TRUE),
          zoom = 10) %>%
  addScaleBar(position = "topleft") %>%
  addCircleMarkers(data= nash_venue_data,
                   lng=~x, 
                   lat=~y,
                   radius =~ 1, 
                   fillOpacity =~ 1,
                   color =~ "blue",
                   label=~paste(name, address_admin.x))

l

```
### 4.2.2. Heat map (ggplot)

NOTE - needs a spatial data layer for the county behind it.

```{r make_fishnet}
fishnet <- st_make_grid(d1_aggregates_nash %>%
                          st_transform(crs = 2274), 
                        cellsize = 5280) %>% #size in feet - half mile
  st_sf() %>%
  st_transform(crs = 4326)

fishnet <- fishnet[d1_aggregates_nash %>%
                          st_transform(crs = 4326),] %>%
  mutate(uniqueID = rownames(.)) %>%
  select(uniqueID) %>%
  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         lat=map_dbl(geometry, ~st_centroid(.x)[[2]]))

# Join the fishet to the points

fishnet <- st_join(fishnet, 
                nash_venue_data %>%
                  filter(is.na(x)== FALSE,
                         is.na(y)== FALSE) %>%
                  st_as_sf(coords = c("x", "y"), crs = 4326), 
                join = st_intersects, 
                left = TRUE) %>%
  select(uniqueID, X) %>%
  group_by(uniqueID) %>% 
  summarise(n_venues = n_distinct(X, na.rm = TRUE)) %>%
  #mutate(n = ifelse(n == 1, 0, n)) %>%
  #rename(n_venues = n) %>%
  as.data.frame() %>%
  select(-geometry) %>%
  left_join(fishnet, .)
```

```{r fishnet_map, warning = FALSE, message = FALSE}

# Make sure you set the labels here to reflect the actual max density by cell

max(fishnet$n_venues)

ggplot()+
  geom_sf(data = d1_aggregates_nash,
          fill = '#f0f0f0', 
          color = 'white')+
  geom_sf(data = fishnet %>%
            filter(n_venues >0), 
          aes(fill = n_venues),
          color = "transparent",
          alpha = 0.4)+
  scale_fill_viridis('VENUES/\nmi^2', direction = -1,
                     limits=c(1,max(fishnet$n_venues)), breaks=c(1, max(fishnet$n_venues)),
                     labels=c("1",max(fishnet$n_venues)))+
  labs(
    title = "VENUE DENSITY - Nashville, 2023",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

```{r fishnet_w_basemap}
ggmap(base_map1) +
 geom_sf(data = ll(fishnet %>%
            filter(n_venues >0)),
            inherit.aes = TRUE,
          aes(fill = n_venues),
          color = "transparent",
          alpha = 0.4)+
  scale_fill_viridis('VENUES/\nmi^2', direction = -1,
                     limits=c(1,max(fishnet$n_venues)), breaks=c(1, max(fishnet$n_venues)),
                     labels=c("1",max(fishnet$n_venues)))+
  labs(
    title = "VENUE DENSITY - Nashville / Davidson County, 2023",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

### 4.2.3. Point Map (static)


### 4.2.4. Map by Planning District (count)

TO DO ONCE d1_aggregates_nash is set


## 4.3. IMV Status

## 4.3.1. Independent Ownership

```{r}
ggplot(data = nash_venue_data %>%
         filter(is.na(ownership_structure) == FALSE))+
  geom_bar(aes(ownership_structure), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Q: Is the venue independently owned and operated?",
    subtitle = "Independence - no association with another business through common ownership\n or affiliation (sharing of employees, resources, branding etc.,)",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme
```

## 4.3.2. Corporate Function

```{r}
ggplot(data = nash_venue_data %>%
         filter(is.na(independent_booking) == FALSE))+
  geom_bar(aes(independent_booking), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Are booking or promotion contracted to corporate partners? ",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme
```

```{r}
ggplot(data = nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(IMV), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "IMV Status",
    subtitle = "Independent Ownership Structure and Independent Booking & Promotion",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme
```

```{r}
ggplot(data = nash_venue_data %>%
         mutate(ownership_structure = ifelse(ownership_structure == "1. Yes",
                                             "Independently Owned & Operated", 
                                             "Non-Indie Owned or No Data")))+
  geom_bar(aes(independent_booking), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "IMV Status",
    subtitle = "Are booking or promotion contracted to corporate partners?",
    x="Facetted by Ownership Structure",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~ownership_structure)+
  plotTheme
```

## 4.4. Capacity

### 4.4.1. Histogram of capacity

```{r community_histogram}
ggplot(data = nash_venue_data %>%
         mutate(capacity = as.numeric(capacity)) %>%
         filter(capacity < 5000))+
  geom_histogram(aes(capacity), fill = CityPalette[6], alpha = 0.6, binwidth = 250)+
  #scale_fill_viridis_d()+
  labs(
    title = "Capacity",
    subtitle = "Capacities Over 5000 are removed",
    x="",
    y="Occupants",
    #fill = "CFP City",
    caption = "Data: Nashville Fire Dept")+
  plotTheme

```

### 4.4.2. Capacity by IMV status

```{r}
ggplot(data = nash_venue_data %>%
         mutate(capacity = as.numeric(capacity)) %>%
         filter(capacity < 5000) %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_histogram(aes(capacity), fill = CityPalette[6], alpha = 0.6, binwidth = 250)+
  #scale_fill_viridis_d()+
  labs(
    title = "Capacity",
    subtitle = "Capacities Over 5000 are removed",
    x="",
    y="Occupants",
    #fill = "CFP City",
    caption = "Data: Nashville Fire Dept")+
  facet_wrap(~IMV)+
  plotTheme
```

```{r}
nash_venue_data %>%
         mutate(capacity = as.numeric(capacity)) %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")) %>%
  group_by(IMV) %>%
  summarize(total_capacity = sum(capacity, na.rm = TRUE),
            median_capacity = median(capacity, na.rm = TRUE)) %>%
  kable() %>%
  kable_styling()

```

### 4.4.3. Geography of Occupancy

- Map of occupancies (e.g. occupant load per fishnet cell or per planning area)

## 4.5. Venue Age

```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(years_operating), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Years Operating",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(years_operating), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Years Operating",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

## 4.6. Events Per Month

```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(events_per_month), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Events Per Month",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(events_per_month), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Events Per Month",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

## 4.7. Artist Payment

```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(funding_source), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Means of Payment",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(funding_source), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Means of Payment",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

## 4.6. Programming

- Bar plots of programming variables (facetted by indie/non)

### 4.6.1. Experimentation

```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(experimentation), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Experimentation Likelihood",
    subtitle = "Q: Compared to other venues in the city: Is this venue a platform for niche or experimental trends, sounds and art forms? Is it a place for experimental performers or extraordinary event concepts?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(experimentation), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Experimentation Likelihood",
    subtitle = "Q: Compared to other venues in the city: Is this venue a platform for niche or experimental trends, sounds and art forms? Is it a place for experimental performers or extraordinary event concepts?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

### 4.6.2. Music as Main Purpose

```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(purpose), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Main Purpose",
    subtitle = "Q: Is the music program the main purpose why people attend this venue, and not e.g. food, drink, products?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(purpose), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Main Purpose",
    subtitle = "Q: Is the music program the main purpose why people attend this venue, and not e.g. food, drink, products?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```


### 4.6.3. Interdisciplinarity

```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(interdisciplinarity), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Interdisciplinarity",
    subtitle = "Q: Does the venue offer events for non-music presentations, such visual art, performing art, panel discussions or film screenings?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(interdisciplinarity), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Interdisciplinarity",
    subtitle = "Q: Does the venue offer events for non-music presentations, such visual art, performing art, panel discussions or film screenings?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

### 4.6.4. Community Focus


```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(community_focus), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Community Focus",
    subtitle = "Q: Is the venue likely to be any of the following... a consistent platform for a niche genre, a space for underrepresented communities or music scenes, a neighbourhood community hub, and not e.g. walk in tourists?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(community_focus), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Community Focus",
    subtitle = "Q: Is the venue likely to be any of the following... a consistent platform for a niche genre, a space for underrepresented communities or music scenes, a neighbourhood community hub, and not e.g. walk in tourists?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

### 4.6.5. Promoting Events


```{r}

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(event_promotion), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Promoting Artistic Content",
    subtitle = "Q: Is the promotion and marketing of this space focused on artistic content (artists, lineups, performances)?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")))+
  geom_bar(aes(event_promotion), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Interdisciplinarity",
    subtitle = "Q: Is the promotion and marketing of this space focused on artistic content (artists, lineups, performances)?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```


## 4.7. CFP Comparisons

- How do some important metrics compare to other cities in CFP database?

# 5. Venues and The City

- Venue zoning districts (bar plot)

- Venue square foot sales values and gross sales values (histogram, inflation adjusted)



- Venues by planning area / neighborhood

All music spaces

```{r venues_total_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(venue_count) == FALSE),
          aes(fill = venue_count),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Venue Count', direction = -1, alpha = 0.8)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r venues_full_indie_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(venue_count) == FALSE),
          aes(fill = venue_count),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Venue Count', direction = -1, alpha = 0.8)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

- Surface map of real estate values by square foot with indie venues on top (this is found later)

- k=5 mean square footage costs of recent sales (inflation adjusted) for indies

- Relationship between programming scores and real estate value

- Comparison to CFP cities - programming and real estate relationships

- Programming, cost and relationship to distance to CBD

- Venue age by district - where are the young and old venues?

- CFP indicators maps

```{r experimentation}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(experimentation) == FALSE),
          aes(fill = experimentation),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Mean Experimental\nContent Score', direction = -1)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r community_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(community_focus) == FALSE),
          aes(fill = community_focus),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Mean Community\nFocus Score', direction = -1)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r experimental_plot}

ggplot(data = d1_aggregates_nash %>%
         filter(is.na(experimentation) == FALSE) %>%
         as.data.frame() %>%
         mutate(venue_text = str_c(as.character(venue_count), " venues")) %>%
         select(venue_text, venue_count, experimentation, d1_name) %>%
         arrange(-experimentation) %>%
         top_n(10))+
  geom_bar(aes(x = reorder(toupper(d1_name), experimentation), 
               y= experimentation),
           stat = "identity", fill = CityPalette[6], width = 0.3,
           alpha = 0.8)+
  geom_text(aes(label = toupper(venue_text), x = toupper(d1_name), 
                y= experimentation / 2), alpha = 0.6, size = 4 )+
  labs(
    title = "DISTRICTS WITH HIGHEST EXPERIMENTAL CONTENT SCORES",
    #subtitle = "Labels indicate total number of districts in that ward",
    caption = "Data: PennPraxis")+
  ylab("MEAN EXPERIMENTAL CONTENT SCORE (SCALE OF 1-4)")+
  xlab("")+
  coord_flip()+
  plotTheme

```

```{r experimental_plot}

ggplot(data = d1_aggregates_nash %>%
         filter(is.na(community_focus) == FALSE) %>%
         as.data.frame() %>%
         mutate(venue_text = str_c(as.character(venue_count), " venues")) %>%
         select(venue_text, venue_count, community_focus, d1_name) %>%
         arrange(-community_focus) %>%
         top_n(10))+
  geom_bar(aes(x = reorder(toupper(d1_name), community_focus), 
               y= community_focus),
           stat = "identity", fill = CityPalette[6], width = 0.3,
           alpha = 0.8)+
  geom_text(aes(label = toupper(venue_text), x = toupper(d1_name), 
                y= community_focus / 2), alpha = 0.6, size = 4 )+
  labs(
    title = "DISTRICTS WITH HIGHEST COMMUNITY SCORES",
    #subtitle = "Labels indicate total number of districts in that ward",
    caption = "Data: PennPraxis")+
  ylab("MEAN COMMUNITY PROGRAM SCORE (SCALE OF 1-4)")+
  xlab("")+
  coord_flip()+
  plotTheme

```

# 6. Venues and Regulation

- What kind of licenses are associated with these venues?

- What about the ones that primarily hold shows (e.g. 10+ per month)

# 7. Venues and Threats

- What are the venues listed as threatened, where are they? (map) What are their characteristics?

```{r}
nash_venue_data %>%
  filter(threats_neighbors == 1 |
           threats_cost == 1 |
           threats_licensing == 1) %>%
  select(name, address_admin, APN, threats_neighbors, threats_cost, threats_licensing) %>%
  kable() %>%
  kable_styling()
  
```

- What properties have the highest disparity between estimated square footage value and assessed value?

# 8. Change in Nashville

- Map of change in rents by census tract (over 10 years)

- Price per sqft by grid cell in Nashville (based on cadastral data)

```{r}
parcels = st_read("~/Github/Nashville_IMV/data/metro/Nashville_Parcel_data.shp") %>% st_transform(4326)
```

Filtering non-zero sales since 2020, joining to fishnet and averaging sales price by sq footage

```{r}
fishnet_parcels <- st_make_grid(d1_aggregates_nash %>%
                          st_transform(crs = 2274), 
                        cellsize = 5280) %>% #size in feet - half mile
  st_sf() %>%
  st_transform(crs = 4326)

fishnet_parcels <- fishnet_parcels[d1_aggregates_nash %>%
                          st_transform(crs = 4326),] %>%
  mutate(uniqueID = rownames(.)) %>%
  select(uniqueID) %>%
  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         lat=map_dbl(geometry, ~st_centroid(.x)[[2]]))

# Join the fishet to the points

fishnet_parcels <- st_join(fishnet_parcels, 
                parcels %>%
                  filter(SalePrice > 0,
                         year(ymd(OwnDate))> 2020,
                         st_is_valid(.)) %>%
                  #sample_n(1000) %>%
                  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                         lat=map_dbl(geometry, ~st_centroid(.x)[[2]])) %>%
                  filter(is.na(lon)== FALSE,
                         is.na(lat)== FALSE) %>%
                  st_as_sf(coords = c("lon", "lat"), crs = 4326), 
                join = st_intersects, 
                left = TRUE) %>%
  select(uniqueID, TotlAppr, starea) %>%
  group_by(uniqueID) %>% 
  summarise(medianAssessment = median(TotlAppr/starea, na.rm = TRUE)) %>%
  #mutate(n = ifelse(n == 1, 0, n)) %>%
  #rename(n_venues = n) %>%
  as.data.frame() %>%
  select(-geometry) %>%
  left_join(fishnet_parcels, .)
```

```{r fishnet_map, warning = FALSE, message = FALSE}

# Make sure you set the labels here to reflect the actual max density by cell

max(fishnet_parcels$medianAssessment)

ggplot()+
  geom_sf(data = fishnet_parcels %>%
            filter(is.na(medianAssessment) == FALSE), 
          aes(fill = medianAssessment),
          color = "transparent",
          alpha = 0.4)+
 scale_fill_viridis('Price sqft', direction = -1)+
  geom_sf(data = d1_aggregates_nash %>%
            st_transform(4326), fill = "transparent")+
  geom_point(data = nash_venue_data %>%
         mutate(IMV = ifelse(independent_booking == "3. Never" &
                                        ownership_structure == "1. Yes",
                                      "IMV",
                                      "Non-IMV")) %>%
           filter(IMV == "IMV"),
             aes(x = x, y = y, color = IMV),
             size = 1.75,
             alpha = 0.5)+
  labs(
    title = "Median Sale Price per Square Foot, 2021-23",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

- Identification of development "hot spots" and related venues

- What are the areas of opportunity (e.g. can we ID relatively lower rent areas with high percentages of young adults, reasonable proximity to downtown?)

# 9. Maps for report

- Venue profile accompaniments (shows parcel and neighborhood context)

Here is an example - make a ggbasemap with a specific buffer area around the parcel (identified in the code by APN) and then just map the parcel.

```{r}
base_map_3rd_and_lindsley <-get_stamenmap(bbox = unname(st_bbox(ll(st_buffer(st_centroid(nash_venue_data %>%
                                                                                filter(name == "3rd & Lindsley") %>%
                                                                                  st_as_sf(coords = c("x", "y"), crs = 4269) %>% st_transform(4326)),
                                                                  300)))),
                    force = TRUE, maptype = "toner-lite", zoom = 16)
```

```{r}
ggmap(base_map_3rd_and_lindsley) +
 geom_sf(data = ll(nash_venue_data %>%
                     filter(name == "3rd & Lindsley") %>%
                     st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326)),
            inherit.aes = FALSE, 
         color = "red",
         size = 2)+
  labs(
    title = "Focus Venue - 3rd and Lindsley",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

```{r}
ggmap(base_map_3rd_and_lindsley) +
 geom_sf(data = ll(right_join(parcels,
                             nash_venue_data %>%
                     filter(name == "3rd & Lindsley")) %>%
                     st_transform(4326)),
            inherit.aes = FALSE, 
         color = "red",
         fill = "red",
         alpha = 0.4)+
  labs(
    title = "Focus Venue - 3rd and Lindsley",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

- Broader context maps (e.g. whole city with venues and some basemap stuff?)

- Area maps for any geographic focus (e.g. North Nashville)