---
title: "Nashville Venues Project Data Portal"
author: "Michael Fichman & Sofia Fasullo for PennPraxis"
date: "8/29/2023"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: cosmo
    code_folding: hide
    code_download: no
  pdf_document:
    toc: yes
---


NOTES AND TO-DO's:

Week of 9/6

- Associate license data with venues in a separate script (Sofia) - by 9/15

Week of 9/13

- Write a methodology and data sources section (Sofia)
- Annotate maps and charts, put proper text and styling (Sofia)
- Write top takeaways (Michael)
- K-means spatial clustering (Michael) - DONE
- Fix some venue data points - before re-running with licenses:

Nissan Stadium events/month, 3rd and Lindsley independence

Week of 9/20

- Create graphics for each venue zoom in - see end of document
- Create some general census maps, tables, figures to illustrate economic geography in Nashville and changes (Sofia)


Unknown timeframe

- Add capacity data and re-run data_markdown with "venue ladder" and cfp comparison (TBD - ??)
- Render graphics for document


Recently finished:

- Add property condition, year built, building use and other data in the data_markdown (Michael) DONE
- Analyze recent sales values and impart risk scores (Michael) - DONE
- Do some comparisons with CFP database (Michael) - DONE


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# ---- Load Packages ----
#list of packages


library(tidyverse)
library(data.table)
library(sf)
library(viridis)
library(viridisLite)
#library(translateR)
library(kableExtra)
library(leaflet)
library(leaflet.extras)
library(lubridate)
library(mapview)
library(DT)

# ---- Load Graphic Palettes ----

# Load a ggplot theme and a color palette

plotTheme <- theme(
  plot.title =element_text(size=12),
  plot.subtitle = element_text(size=8),
  plot.caption = element_text(size = 6),
  axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
  axis.text.y = element_text(size = 10),
  axis.title.y = element_text(size = 10),
  # Set the entire chart region to blank
  panel.background=element_blank(),
  plot.background=element_blank(),
  #panel.border=element_rect(colour="#F0F0F0"),
  # Format the grid
  panel.grid.major=element_line(colour="#D0D0D0",size=.75),
  axis.ticks=element_blank())

mapTheme <- theme(plot.title =element_text(size=12),
                  plot.subtitle = element_text(size=8),
                  plot.caption = element_text(size = 6),
                  axis.line=element_blank(),
                  axis.text.x=element_blank(),
                  axis.text.y=element_blank(),
                  axis.ticks=element_blank(),
                  axis.title.x=element_blank(),
                  axis.title.y=element_blank(),
                  panel.background=element_blank(),
                  panel.border=element_blank(),
                  panel.grid.major=element_line(colour = 'transparent'),
                  panel.grid.minor=element_blank(),
                  legend.direction = "vertical", 
                  legend.position = "right",
                  plot.margin = margin(1, 1, 1, 1, 'cm'),
                  legend.key.height = unit(1, "cm"), legend.key.width = unit(0.2, "cm"))

palette <- c("#10142A", "#47E9B9", "#F55D60", "#71EA48", "#C148EA", "#EAC148")
viridisPalette <- c("#440154", "#73D055", "#F55D60", "#238A8D", "#FDE725")
CityPalette <- c("#A230C2", "#3AEAB8", "#F9C700", "#0069FC", "#EF3340", "#bdbdbd") # Berlin, NYC, Tokyo, Stockholm, Montreal, Sydney
```

```{r load_cfp_data, message=FALSE, warning=FALSE, results = 'hide'}

# LOAD IN THE CFP DATA FOR COMPARISONS

# Read in district aggregates
d1_aggregates <- st_read("~/GitHub/CFP/unified__city_data/district_aggregates/d1_aggregates_11_16_22.geojson") %>%
  st_as_sf(crs = 4326)

d2_aggregates <- st_read("~/GitHub/CFP/unified__city_data/district_aggregates/d2_aggregates_06_15_23.geojson") %>%
  st_as_sf(crs = 4326) %>%
  rename(d2_name = d2_name.x)


# Read in venues
main_venue_data <- read.csv("~/GitHub/CFP/unified__city_data/main_venue_data_final_testSydney.csv") %>%
  mutate(city = ifelse(city == "Solna", "Stockholm", city))

# Read in EPSG information

source("~/GitHub/CFP/unified__city_data/epsg_list.R")


```

```{r load_nash_data, message=FALSE, warning=FALSE, results = 'hide'}

# LOAD IN THE NASH DATA

# Read in district aggregates
d1_aggregates_nash <- st_read("~/GitHub/Nashville_IMV/data/venue_tables/to_map/d1_aggregate_v5.geojson") %>%
  st_as_sf(crs = 4326) %>%
  rename(venue_count = num_venues,
         d1_name = Communit_1)

d2_aggregates_nash <- st_read("~/GitHub/CFP/unified__city_data/district_aggregates/d2_aggregates_06_15_23.geojson") %>%
  st_as_sf(crs = 4326) %>%
  rename(d2_name = d2_name.x)


# Read in venues - THIS IS THE FILEPATH IN Data_Markdown.Rmd as of 7/18/2023
nash_venue_data <- st_read("~/GitHub/Nashville_IMV/data/venue_tables/to_map/venues_v4.geojson") %>%
  st_transform(crs = 4326) %>%
  group_by(name) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(x=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         y=map_dbl(geometry, ~st_centroid(.x)[[2]])) %>%
  mutate(X = row_number()) %>%
  as.data.frame()


```

```{r create_basemaps}
library(ggmap)


ll <- function(dat, proj4 = 4326){
st_transform(dat, proj4)
}
```

```{r message = FALSE}
base_map1 <-get_stamenmap(bbox = unname(st_bbox(ll(st_buffer(st_centroid(d1_aggregates_nash),10000)))),
                    force = TRUE, maptype = "toner-lite", zoom = 11)

```

```{r functions, include=FALSE}
#function to calculate the distribution of values in any given column with the option to group by another column
calculate_share <- function(dat, col, facetCol = "") {
  if(facetCol != ""){
    dat <- dat %>%
                  group_by(!!sym(col), !!sym(facetCol)) %>% 
                  summarise(count = n()) %>% 
                  group_by(!!sym(facetCol)) %>%
                  mutate(share = count/sum(count)*100)
  }
  else {
    dat <- dat %>% 
                  group_by(!!sym(col)) %>% 
                  summarize(count = n()) %>% 
                  mutate(share = count/sum(count)*100)
  }
  return(dat)
}
```

# 1. Key Takeaways

## 1.1. Venue database characteristics

- Researchers, community members, and focus group experts identified 253 spaces used for music in Nashville on a periodic or regular basis (Section 4). 114 of these were identified as being "Music Spaces", where music is likely to be the primary offer, and events are held more than once per week. The remainder (139) were considered "Occasional Music Spaces" (Section 4.1.2)

- 23 of these Music Spaces (and 14 Occasional Music Spaces) were identified by researchers, community members, and focus group experts as likely to be IMVs (Completely independent ownership and operations). 50 Music Spaces were identified as being "Quasi-Independent" because some of their functions were assessed as likely to be contracted to corporate outside entities or they had legal ownership affiliations to other businesses. 41 Music Spaces were assessed as likely to be completely non-independent. 

## 1.2. Community programming assessment

- Community members and focus group experts assessed the likelihood of different types of program characteristics as a way to understand how locally or artistically focused the venue's cultural offer was likely to be. Although this is an obviously subjective exercise, it allows a broad understanding of how Nashvillians understand the nature of programming in the city's venues.

- IMVs were, on average, more likely to present experimental programming than Quasi-Independent or Non-Independent music spaces. However, amongst all venue classifications, experimental programming was seen as generally unlikely to be presented in Nashville venues. Compared to VibeLab/Praxis' Creative Footprint venue survey (which collects the same metric), Nashville venues were, on average ranked lowest for experimental likelihood amongst all 7 cities.

- IMVs are, on average, more likely to present community-focused programming than Quasi-Independent or Non-Independent music spaces.

- IMVs are, on average, more likely to promote lineups and artists in their marketing than Quasi-Independent or Non-Independent music spaces.

- Non-Independent venues were assessed to be dramatically more likely to put on non-music programming - including talks, films, panel discussions or other types of entertainment-driven, non-music uses. IMVs and Quasi-IMVs seem to be more likely to focus on music as a singular program type.

## 1.3. Economic Geography

- Spaces with lower land values are observed to be more likely to present community-oriented and experimental programming (IMV or not)

- The core of Nashville's live music cluster is dominated by non-IMVs. IMVs on average, locate further away from the center of the cluster. This is the area most frequented by tourists and best served by regional transportation.

- IMVs are in spaces valued at far less per sqft than non-IMVs. 

- Although the core of the Nashville live music cluster is Downtown, IMVs are most concentrated in East Nashville. 

- Concentration by districts, programming by districts, co-location with young adults (by district)

- IMVs, by location, are exposed to less real estate risk (high localized sales volumes, high ratio of area land value to venue land value) than non-IMV Music Spaces. This perhaps a result of recent closures reducing the number of IMVs in high

## 1.4. Land Use, Regulation and Building Characteristics

- Live music is played in an extraordinary variety of contexts in Nashville - in concert halls and auditoriums, but also in strip malls, restaurants, and stores, mixed use complexes with apartments or offices, hotels and even on docks and marinas. Most of the time, when music is being played, it's on land that is primarily being designated for use as something else. IMVs and Quasi-IMVs are more likely to be in bar/nightclub, restaurant or retail contexts, whereas Non-Independents span a very wide variety of uses, including large format industrial reuse and institutional spaces.

- Zoning - what are the types we are seeing SOPHIA CAN YOU CHECK ON THE ZONING DESCRIPTIONS?

- Building quality - building stock was generally listed as being "Average" with a small few exceptions.

- Capacities

- Licensing - what kind of licenses

## 1.5. Multi-City Comparison with CFP Database

- Amongst CFP cities - Nashville has a profile most similar to that of Stockholm - relatively low scores on experimentation, community program - but it was ranked comparatively well on the fact that venues promote music as a core offer. This comparison is based on all of the music spaces collected in in the community process, not just the regular music spaces (other CFP city databases also consist of spaces that host music a minimum of once per month)

## 1.7. US Census Analysis

TBD

# 2. Data Sources

- IMV data set

- Chamber of Commerce Data (link)

- US Census

- Nashville Metro Cadastral

- Nashville Metro Parcels, Property Characteristics

- Nashville Metro Fire Inspection Data

- Nashville Planning Districts

# 3. Methods

What did we do?

We collected the data set with liaisons, community members and desk research (this will be covered by VL in the report)

We related each venue to it's APN number (a property identifier) and joined it to tax records, license records.

We created variables for knn sq ft costs, dist to CBD centroid, joined venues to districts

# 4. Venue Database

Let's give descriptive statistics for the venue database

Searchable database

```{r}
datatable(nash_venue_data, 
          options = list(pageLength = 10))
```

## 4.1. Total number of venues

- How many venues

```{r}
nrow(nash_venue_data)

```

### 4.1.2. Number of IMVs


What is a dedicated music venue?  What is an independent music venue?

A music space - 
More than 1 show per week (5+ per month), is live music the purpose rated "somewhat likely" or "very likely"

```{r}
nash_venue_data %>%
  group_by(music_space) %>%
  tally()

```

```{r}
nash_venue_data %>%
  group_by(music_space, IMV) %>%
  tally()

```

## 4.2. Venue locations

Music spaces

```{r}
ggplot()+
    geom_sf(data = d1_aggregates_nash,
          fill = '#f0f0f0', 
          color = 'white')+
  geom_point(data = nash_venue_data,
             aes(x = x, y = y, color = music_space),
             alpha = 0.3, size = 1)+
  mapTheme

```

Music spaces by indepenence

```{r}
ggplot()+
    geom_sf(data = d1_aggregates_nash,
          fill = '#f0f0f0', 
          color = 'white')+
  geom_point(data = nash_venue_data %>%
               filter(music_space == "Music Space"),
             aes(x = x, y = y),
             alpha = 0.3, size = 1)+
  facet_wrap(~IMV)+
  mapTheme

```

### 4.2.1. Interactive Map 

```{r leaflet, message= FALSE, warning=FALSE, eval = FALSE}

l <- leaflet() %>% 
  addProviderTiles(providers$Esri.WorldTopoMap) %>%
  setView(lng = mean(nash_venue_data$x, na.rm = TRUE),
          lat = mean(nash_venue_data$y, na.rm = TRUE),
          zoom = 10) %>%
  addScaleBar(position = "topleft") %>%
  addCircleMarkers(data= nash_venue_data,
                   lng=~x, 
                   lat=~y,
                   radius =~ 1, 
                   fillOpacity =~ 1,
                   color =~ "blue",
                   label=~paste(name, address_admin, IMV))

l

```

```{r}
nash_venue_data %>%
  st_as_sf(coords = c("x","y"), 
           crs= 4326) %>%
  filter(music_space == "Music Space") %>%
  select(name, address_admin, APN, IMV, ownership_structure, independent_booking, capacity, TotlAppr) %>%
  mapView(., zcol = "IMV")

```
### 4.2.2. Heat map (ggplot)

This is JUST  FOR MUSIC SPACES, does not include occasional music spaces

```{r make_fishnet}
fishnet <- st_make_grid(d1_aggregates_nash %>%
                          st_transform(crs = 2274), 
                        cellsize = 5280) %>% #size in feet - half mile
  st_sf() %>%
  st_transform(crs = 4326)

fishnet <- fishnet[d1_aggregates_nash %>%
                          st_transform(crs = 4326),] %>%
  mutate(uniqueID = rownames(.)) %>%
  select(uniqueID) %>%
  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         lat=map_dbl(geometry, ~st_centroid(.x)[[2]]))

# Join the fishet to the points

fishnet <- st_join(fishnet, 
                nash_venue_data %>%
                  filter(is.na(x)== FALSE,
                         is.na(y)== FALSE) %>%
                  filter(music_space == "Music Space") %>%
                  st_as_sf(coords = c("x", "y"), crs = 4326), 
                join = st_intersects, 
                left = TRUE) %>%
  select(uniqueID, X) %>%
  group_by(uniqueID) %>% 
  summarise(n_venues = n_distinct(X, na.rm = TRUE)) %>%
  #mutate(n = ifelse(n == 1, 0, n)) %>%
  #rename(n_venues = n) %>%
  as.data.frame() %>%
  select(-geometry) %>%
  left_join(fishnet, .)
```

```{r fishnet_map, warning = FALSE, message = FALSE}

# Make sure you set the labels here to reflect the actual max density by cell

max(fishnet$n_venues)

ggplot()+
  geom_sf(data = d1_aggregates_nash,
          fill = '#f0f0f0', 
          color = 'white')+
  geom_sf(data = fishnet %>%
            filter(n_venues >0), 
          aes(fill = n_venues),
          color = "transparent",
          alpha = 0.4)+
  scale_fill_viridis('VENUES/\nmi^2', direction = -1,
                     limits=c(1,max(fishnet$n_venues)), breaks=c(1, max(fishnet$n_venues)),
                     labels=c("1",max(fishnet$n_venues)))+
  labs(
    title = "VENUE DENSITY - Nashville, 2023",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

```{r fishnet_w_basemap}
ggmap(base_map1) +
 geom_sf(data = ll(fishnet %>%
            filter(n_venues >0)),
            inherit.aes = TRUE,
          aes(fill = n_venues),
          color = "transparent",
          alpha = 0.4)+
  scale_fill_viridis('VENUES/\nmi^2', direction = -1,
                     limits=c(1,max(fishnet$n_venues)), breaks=c(1, max(fishnet$n_venues)),
                     labels=c("1",max(fishnet$n_venues)))+
  labs(
    title = "VENUE DENSITY - Nashville / Davidson County, 2023",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

### 4.2.3. Point Map (static)


### 4.2.4. Map by Planning District (count)

TO DO ONCE d1_aggregates_nash is set


## 4.3. IMV Status

## 4.3.1. Independent Ownership

```{r}
ggplot(data = nash_venue_data %>%
         filter(is.na(ownership_structure) == FALSE))+
  geom_bar(aes(ownership_structure), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Q: Is the venue independently owned and operated?",
    subtitle = "Independence - no association with another business through common ownership\n or affiliation (sharing of employees, resources, branding etc.,)",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~music_space)+
  plotTheme
```

## 4.3.2. Corporate Function

```{r}
ggplot(data = nash_venue_data %>%
         filter(is.na(independent_booking) == FALSE))+
  geom_bar(aes(independent_booking), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Are booking or promotion contracted to corporate partners? ",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~music_space)+
  plotTheme
```

```{r}
ggplot(data = nash_venue_data)+
  geom_bar(aes(IMV), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "IMV Status",
    subtitle = "Independent Ownership Structure and Independent Booking & Promotion",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~music_space)+
  coord_flip()+
  plotTheme
```

## 4.4. Capacity

### 4.4.1. Histogram of capacity

NOTE - These data are not complete as of 9/5 - we are awaiting data from Nash FD - these are data from the Chamber's study several years ago.

```{r community_histogram}
ggplot(data = nash_venue_data %>%
         mutate(capacity = as.numeric(capacity)) %>%
         filter(capacity < 5000))+
  geom_histogram(aes(capacity), fill = CityPalette[6], alpha = 0.6, binwidth = 250)+
  #scale_fill_viridis_d()+
  labs(
    title = "Capacity",
    subtitle = "Capacities Over 5000 are removed",
    x="",
    y="Occupants",
    #fill = "CFP City",
    caption = "Data: Nashville Fire Dept")+
  plotTheme

```

### 4.4.2. Capacity by IMV status

```{r}
ggplot(data = nash_venue_data %>%
         mutate(capacity = as.numeric(capacity)) %>%
         filter(capacity < 5000) )+
  geom_histogram(aes(capacity), fill = CityPalette[6], alpha = 0.6, binwidth = 250)+
  #scale_fill_viridis_d()+
  labs(
    title = "Capacity",
    subtitle = "Capacities Over 5000 are removed",
    x="",
    y="Occupants",
    #fill = "CFP City",
    caption = "Data: Nashville Fire Dept")+
  facet_wrap(~IMV)+
  plotTheme
```

There is still a ton of missing capacity data as of 8/16 - MF

```{r}
nash_venue_data %>%
         mutate(capacity = as.numeric(capacity)) %>%
  group_by(IMV) %>%
  summarize(total_capacity = sum(capacity, na.rm = TRUE),
            median_capacity = median(capacity, na.rm = TRUE)) %>%
  kable() %>%
  kable_styling()

```

### 4.4.3. Geography of Occupancy

- Map of occupancies (e.g. occupant load per fishnet cell or per planning area)

## 4.5. Venue Age

```{r}

ggplot(nash_venue_data )+
  geom_bar(aes(years_operating), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Years Operating",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

```

```{r}

ggplot(nash_venue_data )+
  geom_bar(aes(years_operating), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Years Operating",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_grid(music_space~IMV)+
  plotTheme

```

```{r}

ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(years_operating, fill = IMV), position = "dodge", alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Years Operating",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

```

## 4.6. Events Per Month

```{r}

ggplot(nash_venue_data)+
  geom_bar(aes(events_per_month), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Events Per Month - All Spaces",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data %>%
        filter(music_space == "Music Space"))+
  geom_bar(aes(events_per_month), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Events Per Month, Music Spaces",
    subtitle = "",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

## 4.7. Artist Payment

This data isn't any good - scrapping this

## 4.6. Programming

- Bar plots of programming variables (facetted by indie/non)

### 4.6.1. Experimentation

There is a bi-modal effect with experimentation, it's either very experimental or not at all.

Maybe a better question is - what percentage of spaces are consider likely to offer experimental content between IMV/Non/Quasi?

Answer - roughly 40%, higher than Quasi and non-IMV

```{r}

ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(experimentation), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Experimentation Likelihood - Music Spaces",
    subtitle = "Q: Compared to other venues in the city: Is this venue a platform for niche or experimental trends, sounds and art forms? Is it a place for experimental performers or extraordinary event concepts?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme
```


```{r}
ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(experimentation), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Experimentation Likelihood",
    subtitle = "Q: Compared to other venues in the city: Is this venue a platform for niche or experimental trends, sounds and art forms? Is it a place for experimental performers or extraordinary event concepts?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

On average, IMVs are slightly more experimental

```{r}
nash_venue_data %>%
  group_by(IMV, music_space) %>%
  summarize(mean_experimentation = mean(experimentation_ord, na.rm = TRUE),
            n = n()) %>%
  arrange(music_space) %>%
  kable()


```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  group_by(IMV, experimentation) %>%
  tally() %>%
  mutate(pct = 100*(n/sum(n))) %>%
  kable()


```

### 4.6.2. Music as Main Purpose

```{r}

ggplot(nash_venue_data)+
  geom_bar(aes(purpose), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Main Purpose",
    subtitle = "Q: Is the music program the main purpose why people attend this venue, and not e.g. food, drink, products?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

ggplot(nash_venue_data)+
  geom_bar(aes(purpose), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Main Purpose",
    subtitle = "Q: Is the music program the main purpose why people attend this venue, and not e.g. food, drink, products?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```


### 4.6.3. Interdisciplinarity


```{r}
ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(interdisciplinarity), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Interdisciplinarity - Music Spaces",
    subtitle = "Q: Does the venue offer events for non-music presentations, such visual art, performing art, panel discussions or film screenings?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```


```{r}
nash_venue_data %>%
  group_by(IMV, music_space) %>%
  summarize(mean_interdisciplinarity = mean(interdisciplinarity_ord, na.rm = TRUE),
            n = n()) %>%
  arrange(music_space) %>%
  kable()


```

### 4.6.4. Community Focus


```{r}

ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(community_focus), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Community Focus - Music Spaces",
    subtitle = "Q: Is the venue likely to be any of the following... a consistent platform for a niche genre, a space for underrepresented communities or music scenes, a neighbourhood community hub, and not e.g. walk in tourists?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

```


```{r}
ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(community_focus), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Community Focus - Music Spaces",
    subtitle = "Q: Is the venue likely to be any of the following... a consistent platform for a niche genre, a space for underrepresented communities or music scenes, a neighbourhood community hub, and not e.g. walk in tourists?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

Indie venues ARE more local

```{r}
nash_venue_data %>%
  group_by(IMV, music_space) %>%
  summarize(mean_community_focus = mean(community_focus_ord, na.rm = TRUE),
            n = n()) %>%
  arrange(music_space) %>%
  kable()


```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  group_by(IMV, community_focus) %>%
  tally() %>%
  mutate(pct = 100*(n/sum(n))) %>%
  kable()


```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(likely_community_focus = ifelse(str_detect(community_focus, "Somewhat") |
                                           str_detect(community_focus, "Very"),
                                         "Somewhat or Very Likely Community Focus",
                                         "Not At All or Not too Likely")) %>%
  group_by(IMV, likely_community_focus) %>%
  tally() %>%
  mutate(pct = 100*(n/sum(n))) %>%
  kable()


```


### 4.6.5. Promoting Events


```{r}

ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(event_promotion), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Promoting Artistic Content - Music Spaces",
    subtitle = "Q: Is the promotion and marketing of this space focused on artistic content (artists, lineups, performances)?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  plotTheme

```


```{r}
ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(event_promotion), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Promoting Artistic Content - Music Spaces",
    subtitle = "Q: Is the promotion and marketing of this space focused on artistic content (artists, lineups, performances)?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_wrap(~IMV)+
  plotTheme

```

```{r}
ggplot(nash_venue_data)+
  geom_bar(aes(event_promotion), fill = CityPalette[6], alpha = 0.6, size = 3)+
  #scale_fill_viridis_d()+
  labs(
    title = "Promoting Artistic Content",
    subtitle = "Q: Is the promotion and marketing of this space focused on artistic content (artists, lineups, performances)?",
    x="",
    y="Total Venues",
    caption = "Data: PennPraxis")+
  facet_grid(music_space~IMV)+
  plotTheme

```
```{r}
nash_venue_data %>%
  group_by(IMV, music_space) %>%
  summarize(mean_event_promotion = mean(event_promotion_ord, na.rm = TRUE),
            n = n()) %>%
  arrange(music_space) %>%
  kable()


```

## 4.7. CFP Comparisons

```{r}
main_venue_data %>%
  select(city, promotion, community_focus, experimentation) %>%
  rbind(., nash_venue_data %>%
          mutate(city = "Nashville") %>%
          rename(promotion = event_promotion) %>%
          select(city, promotion, community_focus, experimentation)) %>%
  gather(-city, value = "value", key = "variable") %>%
  mutate(value = case_when(str_detect(value, "1") == TRUE ~ "1. Not At All Likely",
                           str_detect(value, "2") == TRUE ~ "2. Not Too Likely",
                           str_detect(value, "3") == TRUE ~ "3. Somewhat Likely",
                           str_detect(value, "4") == TRUE ~ "4. Very Likely")) %>%
  filter(is.na(value) == FALSE,
         city != "") %>%
  ggplot()+
  geom_bar(aes(value))+
  facet_grid(city~variable, scales = "free")+
  plotTheme

```


```{r}
main_venue_data %>%
  select(city, promotion, community_focus, experimentation) %>%
  rbind(., nash_venue_data %>%
          mutate(city = "Nashville") %>%
          rename(promotion = event_promotion) %>%
          select(city, promotion, community_focus, experimentation)) %>%
  gather(-city, value = "value", key = "variable") %>%
  mutate(value = case_when(str_detect(value, "1") == TRUE ~ 1,
                           str_detect(value, "2") == TRUE ~ 2,
                           str_detect(value, "3") == TRUE ~ 3,
                           str_detect(value, "4") == TRUE ~ 4)) %>%
  filter(is.na(value) == FALSE,
         city != "") %>%
  group_by(city, variable) %>%
  summarize(mean_score = mean(value)) %>%
  ggplot()+
  geom_bar(aes(y = mean_score, x = variable, fill = city), stat = "identity", position = "dodge")+
  plotTheme

```

# 5. Venues and The City

- Venue zoning districts (bar plot)

- Median sqft cost by neighborhood

- IMVs with the highest sq ft cost

## 5.1. Venues and real estate costs

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  filter(value_sqft < 1000) %>%
  ggplot()+
  geom_histogram(aes(value_sqft), binwidth = 50) +
  facet_wrap(~IMV)+
  plotTheme

```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  group_by(IMV) %>%
  summarize(median_sqft = median(value_sqft))

```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  group_by(experimentation) %>%
  summarize(median_value_sqft = median(value_sqft, na.rm = TRUE)) %>%
  ggplot()+
  geom_bar(aes(x = experimentation, y = median_value_sqft), stat = "identity")+
  plotTheme

```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  group_by(community_focus) %>%
  summarize(median_value_sqft = median(value_sqft, na.rm = TRUE)) %>%
  ggplot()+
  geom_bar(aes(x = community_focus, y = median_value_sqft), stat = "identity")+
  plotTheme

```

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  group_by(interdisciplinarity) %>%
  summarize(median_value_sqft = median(value_sqft, na.rm = TRUE)) %>%
  ggplot()+
  geom_bar(aes(x = interdisciplinarity, y = median_value_sqft), stat = "identity")+
  plotTheme

```

Seems like IMVs and non-IMVs program similarly in practice vis-a-vis these measures... ON AVERAGE

What about the exceptional examples??

No - it's basically the same!

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(programming_sum = interdisciplinarity_ord + experimentation_ord +
           community_focus_ord + event_promotion_ord) %>%
  ggplot()+
  geom_histogram(aes(programming_sum), binwidth = 1)+
  facet_wrap(~IMV)+
  plotTheme

```

MF - what are these indies with the super high sq footage values?

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(programming_sum = interdisciplinarity_ord + experimentation_ord +
           community_focus_ord + event_promotion_ord) %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  filter(value_sqft < 1000) %>%
  ggplot()+
  geom_point(aes(y = programming_sum, x = value_sqft, color = IMV))+
  geom_smooth(aes(y = programming_sum, x = value_sqft), method = "lm", se = FALSE)+
  plotTheme

```


```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(programming_sum = interdisciplinarity_ord + experimentation_ord +
           community_focus_ord + event_promotion_ord) %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  filter(value_sqft < 1000) %>%
  ggplot()+
  geom_point(aes(y = programming_sum, x = value_sqft))+
  geom_smooth(aes(y = programming_sum, x = value_sqft), method = "lm", se = FALSE)+
  facet_wrap(~IMV)+
  plotTheme

```

## 5.2. Zoning

These are the most coming zoning designations

SOPHIA - can you look up the top 10 of these and see what they actually mean in the code?

```{r}
nash_venue_data %>%
  group_by(ZONE_DESC) %>%
  tally() %>%
  arrange(-n) %>%
  kable() %>%
  kable_styling()

```

## 5.3. Land Use

```{r}
nash_venue_data %>%
  group_by(LUDesc) %>%
  tally() %>%
  arrange(-n) %>%
  kable() %>%
  kable_styling()

```

```{r}
ggplot(nash_venue_data)+
  geom_bar(aes(LUDesc))+
  facet_wrap(~music_space)+
  coord_flip()+
  plotTheme

```

```{r}
ggplot(nash_venue_data %>%
         filter(music_space == "Music Space"))+
  geom_bar(aes(LUDesc))+
  facet_wrap(~IMV)+
  coord_flip()+
  plotTheme

```

## 5.4. Building Age

```{r}
nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  ggplot()+
  geom_histogram(aes(YearBuilt), binwidth = 10)+
  facet_wrap(~IMV)+
  plotTheme
  

```

## 5.5. Building Condition



## 5.6.  Venues by planning area / neighborhood

All music spaces

```{r venues_total_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(num_music_smaces) == FALSE),
          aes(fill = num_music_smaces),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Music Spaces', direction = -1, alpha = 0.8)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r venues_full_indie_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(IMV_n) == FALSE),
          aes(fill = IMV_n),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('IMVs', direction = -1, alpha = 0.8)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r venues_quasi_indie_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(Quasi_IMV_n) == FALSE),
          aes(fill = Quasi_IMV_n),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Quasi IMVs', direction = -1, alpha = 0.8)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```



- k=5 mean square footage costs of recent sales (inflation adjusted) for indies

- Comparison to CFP cities - programming and real estate relationships

- Programming, cost and relationship to distance to CBD

- Venue age by district - where are the young and old venues?

- CFP indicators maps

```{r experimentation}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(experimentation) == FALSE),
          aes(fill = experimentation),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Mean Experimental\nContent Score', direction = -1)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r community_map}
ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = 'transparent', 
          color = 'grey')+
  geom_sf(data = d1_aggregates_nash %>%
            filter(is.na(community_focus) == FALSE),
          aes(fill = community_focus),
          color = 'grey', alpha = 0.6)+
  scale_fill_viridis('Mean Community\nFocus Score', direction = -1)+
  geom_text(data = d1_aggregates_nash %>%
              filter(venue_count != 0) %>%
              mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                     lat=map_dbl(geometry, ~st_centroid(.x)[[2]])),
            aes(x = lon, y = lat, label = d1_name),
            color = "black", size = 3)+
  mapTheme

```

```{r experimental_plot}

ggplot(data = d1_aggregates_nash %>%
         filter(is.na(experimentation) == FALSE) %>%
         as.data.frame() %>%
         mutate(venue_text = str_c(as.character(venue_count), " venues")) %>%
         select(venue_text, venue_count, experimentation, d1_name) %>%
         arrange(-experimentation) %>%
         top_n(10))+
  geom_bar(aes(x = reorder(toupper(d1_name), experimentation), 
               y= experimentation),
           stat = "identity", fill = CityPalette[6], width = 0.3,
           alpha = 0.8)+
  geom_text(aes(label = toupper(venue_text), x = toupper(d1_name), 
                y= experimentation / 2), alpha = 0.6, size = 4 )+
  labs(
    title = "DISTRICTS WITH HIGHEST EXPERIMENTAL CONTENT SCORES",
    #subtitle = "Labels indicate total number of districts in that ward",
    caption = "Data: PennPraxis")+
  ylab("MEAN EXPERIMENTAL CONTENT SCORE (SCALE OF 1-4)")+
  xlab("")+
  coord_flip()+
  plotTheme

```

```{r experimental_plot}

ggplot(data = d1_aggregates_nash %>%
         filter(is.na(community_focus) == FALSE) %>%
         as.data.frame() %>%
         mutate(venue_text = str_c(as.character(venue_count), " venues")) %>%
         select(venue_text, venue_count, community_focus, d1_name) %>%
         arrange(-community_focus) %>%
         top_n(10))+
  geom_bar(aes(x = reorder(toupper(d1_name), community_focus), 
               y= community_focus),
           stat = "identity", fill = CityPalette[6], width = 0.3,
           alpha = 0.8)+
  geom_text(aes(label = toupper(venue_text), x = toupper(d1_name), 
                y= community_focus / 2), alpha = 0.6, size = 4 )+
  labs(
    title = "DISTRICTS WITH HIGHEST COMMUNITY SCORES",
    #subtitle = "Labels indicate total number of districts in that ward",
    caption = "Data: PennPraxis")+
  ylab("MEAN COMMUNITY PROGRAM SCORE (SCALE OF 1-4)")+
  xlab("")+
  coord_flip()+
  plotTheme

```

Venues and Urban Variables by District -

This is not particularly useful compared to the point pattern analysis.

```{r}
d1_aggregates_nash %>%
  as.data.frame() %>%
  select(d1_name, density_venues, IMV_n, avg_med_rent20, avg_dens20, perc_chg_dens, perc_chg_med_rent) %>%
  gather(-d1_name, -density_venues, key = "variable", value = "value") %>%
  ggplot()+
  geom_point(aes(x = value, y = density_venues)) +
  facet_wrap(~variable, scales = "free")+
  plotTheme

```

```{r}
d1_aggregates_nash %>%
  as.data.frame() %>%
  select(d1_name, interdisciplinarity, event_promotion, community_focus, experimentation, avg_med_rent20, avg_dens20, perc_chg_dens, perc_chg_med_rent) %>%
  gather(-d1_name, -interdisciplinarity, -event_promotion, -community_focus, -experimentation, key = "variable", value = "value") %>%
  ggplot()+
  geom_point(aes(x = value, y = experimentation)) +
  geom_line(stat = "smooth", method='lm', 
            aes(y = experimentation, x = value), 
            se = FALSE, 
            linetype = "dashed", alpha = 0.5)+
  facet_wrap(~variable, scales = "free")+
  plotTheme

```

## 5.7. Venues, Programming and Centrality

What is the geometric center of venue activity in Nashville?

```{r}
nash_venue_data %>%
  summarize(centroid_x = mean(x),
            centroid_y = mean(y)) %>%
  ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = "transparent") +
  geom_point(aes(x = centroid_x, y = centroid_y))+
  mapTheme

```

IMVs are located, on average, 2.6 miles from the geographic center of the Nashville venue cluster, while non-IMVs are located, on average, 1.8 miles.

```{r}
centroid_point <- nash_venue_data %>%
  summarize(centroid_x = mean(x),
            centroid_y = mean(y)) %>%
  st_as_sf(coords = c("centroid_x", "centroid_y"), crs = 4326) %>%
  st_transform(2274)

```

```{r}
nash_venue_data %>%
  st_as_sf(crs = 4326) %>%
  st_transform(2274) %>%
  mutate(centroid_dist = st_distance(., centroid_point)) %>%
  filter(music_space == "Music Space") %>%
  as.data.frame() %>%
  group_by(IMV) %>%
  summarize(mean_dist = mean(centroid_dist) / 5280,
            median = median(centroid_dist) / 5280)

```

```{r}

nash_venue_data %>%
  st_as_sf(crs = 4326) %>%
  st_transform(2274) %>%
  mutate(centroid_dist = as.numeric(st_distance(., centroid_point))/5280) %>%
  filter(music_space == "Music Space") %>%
  as.data.frame() %>%
  ggplot()+
  geom_density(aes(centroid_dist, color = IMV))+
  plotTheme

```
## 5.7. Venues and Geographic Clustering

k-means clustering analysis

This first test is a "k-means" cluster analysis that is strictly looking for geographic clusters - this analysis functions by [partitioning a cloud of points in multi-dimensional data to find cluster centroids, and assign each point to a cluster by minimizing within cluster variance](https://en.wikipedia.org/wiki/K-means_clustering).

This is ONLY for music spaces.

This doesn't really produce anything that's much different than the planning areas.

```{r elbow}
set.seed(123)

library(cluster)
library(factoextra)

# function to compute total within-cluster sum of square 
wss <- function(k) {
  kmeans(nash_venue_data %>% 
           filter(music_space == "Music Space", 
                  is.na(y) == FALSE) %>% 
           select(x, y), k, nstart = 10 )$tot.withinss
}

# Compute and plot wss for k = 1 to k = 15
k.values <- 1:15

# extract wss for 2-15 clusters
wss_values <- map_dbl(k.values, wss)

# Run "elbow plot" to determine optimal cluster number.
plot(k.values, wss_values,
       type="b", pch = 19, frame = FALSE, 
       xlab="Number of clusters K",
       ylab="Total within-clusters sum of squares")

# Create a data object with cluster numbers
test <- kmeans(nash_venue_data %>% 
           filter(music_space == "Music Space", 
                  is.na(y) == FALSE) %>% 
            select(x, y), centers = 7, nstart = 25)
```

This interactive map shows the location of these clusters:

```{r leaflet_2}
cluster_data1 <-nash_venue_data %>% 
           filter(music_space == "Music Space", 
                  is.na(y) == FALSE)  %>% 
  cbind(test$cluster) %>% 
  rename(cluster = 'test$cluster')

pal <- colorNumeric(c("red", "blue", "green", "orange", "black", "purple",
                     "yellow", "pink"), 1:8)

l2 <- leaflet() %>% 
  addProviderTiles(providers$Esri.WorldTopoMap) %>%
  setView(lng = mean(cluster_data1$x, na.rm = TRUE),
          lat = mean(cluster_data1$y, na.rm = TRUE),
          zoom = 11) %>%
  addScaleBar(position = "topleft") %>%
  addCircleMarkers(data= cluster_data1,
                   lng=~x, 
                   lat=~y,
                   radius =~ 1, 
                   fillOpacity =~ 1,
                   color = ~pal(cluster),
                   label=~paste(name, address_admin, " | Cluster: ", cluster))

l2
```

# 6. Venues and Regulation

- What kind of licenses are associated with these venues?

- What about the ones that primarily hold shows (e.g. 10+ per month)

# 7. Venues and Threats

- What are the venues listed as threatened, where are they? (map) What are their characteristics?

```{r}
nash_venue_data %>%
  filter(threats_neighbors == 1 |
           threats_cost == 1 |
           threats_licensing == 1) %>%
  select(name, address_admin, APN, threats_neighbors, threats_cost, threats_licensing, Condition, TotlAssd) %>%
  kable() %>%
  kable_styling()
  
```

- What properties have the highest disparity between estimated square footage value and assessed value?

# 8. Change in Nashville

- Map of change in rents by census tract (over 10 years)

## 8.2. Property appraisal values for recent sales

- Price per sqft by grid cell in Nashville (based on cadastral data)

```{r}
parcels = st_read("~/Github/Nashville_IMV/data/metro/Nashville_Parcel_data.shp") %>% st_transform(4326)
```

Filtering non-zero sales since 2020, joining to fishnet and averaging sales price by sq footage

```{r}
fishnet_parcels <- st_make_grid(d1_aggregates_nash %>%
                          st_transform(crs = 2274), 
                        cellsize = 5280/2) %>% #size in feet - half mile
  st_sf() %>%
  st_transform(crs = 4326)

fishnet_parcels <- fishnet_parcels[d1_aggregates_nash %>%
                          st_transform(crs = 4326),] %>%
  mutate(uniqueID = rownames(.)) %>%
  select(uniqueID) %>%
  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
         lat=map_dbl(geometry, ~st_centroid(.x)[[2]]))

# Join the fishet to the points

fishnet_parcels <- st_join(fishnet_parcels, 
                parcels %>%
                  filter(SalePrice > 0,
                         year(ymd(OwnDate))> 2020,
                         st_is_valid(.)) %>%
                  #sample_n(1000) %>%
                  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]),
                         lat=map_dbl(geometry, ~st_centroid(.x)[[2]])) %>%
                  filter(is.na(lon)== FALSE,
                         is.na(lat)== FALSE) %>%
                  st_as_sf(coords = c("lon", "lat"), crs = 4326), 
                join = st_intersects, 
                left = TRUE) %>%
  select(uniqueID, TotlAppr, starea) %>%
  group_by(uniqueID) %>% 
  summarise(medianAppraisal = median(TotlAppr/starea, na.rm = TRUE),
            n_sales = n()) %>%
  #mutate(n = ifelse(n == 1, 0, n)) %>%
  #rename(n_venues = n) %>%
  as.data.frame() %>%
  select(-geometry) %>%
  left_join(fishnet_parcels, .)
```

```{r fishnet_map, warning = FALSE, message = FALSE}

# Make sure you set the labels here to reflect the actual max density by cell

max(fishnet_parcels$medianAppraisal)

ggplot()+
  geom_sf(data = fishnet_parcels %>%
            filter(is.na(medianAppraisal) == FALSE), 
          aes(fill = medianAppraisal),
          color = "transparent",
          alpha = 0.6)+
 scale_fill_viridis('Price sqft', direction = -1)+
  geom_sf(data = d1_aggregates_nash %>%
            st_transform(4326), fill = "transparent")+
  geom_point(data = nash_venue_data %>%
         filter(music_space == "Music Space") %>%
           filter(IMV == "Indep. Owned and Operated"),
             aes(x = x, y = y, color = IMV),
             size = 1.5,
             alpha = 0.5)+
  labs(
    title = "Median Appraised Value per Square Foot, Sales 2021-23",
    subtitle = "Half mile grid",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

## 8.2.1. Venue exposure to real estate risk

Venue Appraised Value / sqft relative to median area appraisal (fishnet cell)

If the value is "above" the y = x line, that means the neighborhood square footage appraisal value of recent sales is higher than the square footage appraisal value of the building.

```{r}
nash_venue_data %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326) %>%
  st_join(., fishnet_parcels) %>%
  filter(value_sqft < 1000) %>%
  filter(music_space == "Music Space") %>%
  ggplot()+
  geom_point(aes(y = value_sqft, x = medianAppraisal))+
  geom_abline(slope = 1)+
  facet_wrap(~IMV)+
  plotTheme

```

What are the most exposed venues as far as ratio of median appraisal to their appraisal?

```{r}
nash_venue_data %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326) %>%
  st_join(., fishnet_parcels) %>%
  as.data.frame() %>%
  filter(music_space == "Music Space") %>%
  mutate(appraisal_ratio = medianAppraisal/value_sqft) %>%
  select(name, appraisal_ratio, value_sqft, address_admin, medianAppraisal, TotlAppr, LUDesc, IMV) %>%
  arrange(-appraisal_ratio) %>%
  kable() %>%
  kable_styling()
```


## 8.2.2. Risk indicators

Total area sales (half mile grid cell), appraised value, appraised value relative to area appraisal median (2021-23), IMV status, programming rating.

Formula:

Risk = sum of:

Quartile Value (amongst music spaces) of:
-Median value of appraisals in sales since 2021 w/in half mile
-Number of sales since 2021 w/in half mile
-Parcel appraised value as a pct of sqft value of sales w/in half mile

Plus:
-Physical condition (1 if average, 2 if fair, 4 if poor or very poor)
Community ranked Programming investment (e.g. experimentation, community focus 1 - 4)

WOULD LIKE TO ADD CAPACITY TO THIS - ALSO ADD COMMUNITY ID'd THREATS

```{r}
risk_matrix <- nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326) %>%
  st_join(., fishnet_parcels) %>%
  mutate(appraisal_ratio = 100*(medianAppraisal/value_sqft)) %>%
  as.data.frame() %>%
  select(appraisal_ratio, experimentation_ord, community_focus_ord,
         name, address_admin, n_sales, medianAppraisal, value_sqft)%>%
  gather(-name, -address_admin, key = "variable", value = "value") %>%
  group_by(variable) %>%
  summarize(quantile = scales::percent(c(0.25, 0.5, 0.75)), 
            quartile = quantile(value, c(0.25, 0.5, 0.75), na.rm = TRUE)) %>%
  spread(quantile, quartile) %>% # join it back to the original data analysis
  left_join(., nash_venue_data %>%
  filter(music_space == "Music Space") %>%
  mutate(value_sqft = TotlAppr/Area_sqft) %>%
  st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326) %>%
  st_join(., fishnet_parcels) %>%
  mutate(appraisal_ratio = 100*(medianAppraisal/value_sqft)) %>%
  mutate(programming_sum = experimentation_ord +
           community_focus_ord + event_promotion_ord) %>%
  as.data.frame() %>%
   select(appraisal_ratio, experimentation_ord, community_focus_ord,
         name, address_admin, n_sales, medianAppraisal, value_sqft)%>%
  gather(-name, -address_admin, key = "variable", value = "value"))%>% 
  mutate(quantile = case_when(value >= `75%` ~ 4,
                              value <= `25%` ~ 1,
                              value > `25%` & value < `50%` ~ 2,
                              value >= `50%` & value < `75%` ~ 3)) %>%
  select(-'25%', -'50%', -'75%') %>%
  group_by(name, address_admin, variable) %>%
  summarize(quantile = quantile) %>%
  pivot_wider(names_from = variable, values_from = quantile) %>%
  left_join(., nash_venue_data %>%
              filter(music_space == "Music Space") %>%
              select(IMV, name, address_admin, APN, music_space, Condition, 
                     threats_neighbors, threats_cost, threats_licensing)) %>%
  mutate(Condition_ord = case_when(str_detect(Condition, "Poor") == TRUE ~ 4,
                                   str_detect(Condition, "Fair") == TRUE ~ 2,
                                   str_detect(Condition, "Average") == TRUE ~ 1,
                                   is.na(Condition) == TRUE ~ 1)) %>%
  mutate(community_threat_assessment = case_when(threats_neighbors + threats_cost + threats_licensing > 1  ~ 4,
                                                 threats_neighbors + threats_cost + threats_licensing == 1  ~ 3,
                                                 threats_neighbors + threats_cost + threats_licensing < 1  ~ 0)) %>%
  mutate(cumulative_risk = sum(appraisal_ratio + Condition_ord + community_threat_assessment +
                                 experimentation_ord + community_focus_ord + value_sqft +
                                 medianAppraisal + n_sales, na.rm = TRUE))

```

```{r}
ggplot(risk_matrix)+
  geom_histogram(aes(cumulative_risk), binwidth = 2)+
  facet_wrap(~IMV)+
  plotTheme

```

```{r}
risk_matrix %>%
  group_by(IMV) %>%
  summarize(mean_risk = mean(cumulative_risk, na.rm = TRUE),
            mean_appraisal_ratio = mean(appraisal_ratio, na.rm = TRUE),
            mean_n_sales = mean(n_sales, na.rm = TRUE),
            meanappraisal = mean(medianAppraisal, na.rm = TRUE))
```

```{r}
  ggplot()+
  geom_sf(data = d1_aggregates_nash, fill = "transparent")+
  geom_point(data = risk_matrix %>%
  left_join(., nash_venue_data %>%
              select(x, y, name, address_admin)) %>%
              mutate(risk_level = case_when(cumulative_risk > 15 ~ "Highest Risk",
                                            cumulative_risk < 15 & cumulative_risk > 10 ~ "Average Risk",
                                            cumulative_risk < 11 ~ "Lowest Risk")) %>%
    filter(is.na(risk_level) == FALSE),
  aes(x = x, y = y), alpha = 0.5, color = "red")+
  facet_grid(risk_level~IMV)+
  mapTheme

```



- What are the areas of opportunity (e.g. can we ID relatively lower rent areas with high percentages of young adults, reasonable proximity to downtown?)

# 9. Maps for report

- Venue profile accompaniments (shows parcel and neighborhood context)

Here is an example - make a ggbasemap with a specific buffer area around the parcel (identified in the code by APN) and then just map the parcel.

## 9.1. 3rd and Lindsley

```{r}
base_map_3rd_and_lindsley <-get_stamenmap(bbox = unname(st_bbox(ll(st_buffer(st_centroid(nash_venue_data %>%
                                                                                filter(name == "3rd & Lindsley") %>%
                                                                                  st_as_sf(coords = c("x", "y"), crs = 4269) %>% st_transform(4326)),
                                                                  300)))),
                    force = TRUE, maptype = "toner-lite", zoom = 16)
```

```{r}
ggmap(base_map_3rd_and_lindsley) +
 geom_sf(data = ll(nash_venue_data %>%
                     filter(name == "3rd & Lindsley") %>%
                     st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326)),
            inherit.aes = FALSE, 
         color = "red",
         size = 2)+
  labs(
    title = "Focus Venue - 3rd and Lindsley",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

```{r}
ggmap(base_map_3rd_and_lindsley) +
 geom_sf(data = ll(right_join(parcels,
                             nash_venue_data %>%
                     filter(name == "3rd & Lindsley")) %>%
                     st_transform(4326)),
            inherit.aes = FALSE, 
         color = "red",
         fill = "red",
         alpha = 0.4)+
  labs(
    title = "Focus Venue - 3rd and Lindsley",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

## 9.2. Eastside Bowl

```{r}
base_map_eastside_bowl <-get_stamenmap(bbox = unname(st_bbox(ll(st_buffer(st_centroid(nash_venue_data %>%
                                                                                filter(name == "Eastside Bowl") %>%
                                                                                  st_as_sf(coords = c("x", "y"), crs = 4269) %>% st_transform(4326)),
                                                                  300)))),
                    force = TRUE, maptype = "toner-lite", zoom = 17)
```

```{r}
ggmap(base_map_eastside_bowl) +
 geom_sf(data = ll(nash_venue_data %>%
                     filter(name == "Eastside Bowl") %>%
                     st_as_sf(coords = c("x", "y"), 
                              crs = 4269) %>%
                     st_transform(4326)),
            inherit.aes = FALSE, 
         color = "red",
         size = 2)+
  labs(
    title = "Focus Venue - Eastside Bowl",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```

```{r}
ggmap(base_map_eastside_bowl) +
 geom_sf(data = ll(right_join(parcels,
                             nash_venue_data %>%
                     filter(name == "Eastside Bowl")) %>%
                     st_transform(4326)),
            inherit.aes = FALSE, 
         color = "red",
         fill = "red",
         alpha = 0.4)+
  labs(
    title = "Focus Venue - 3rd and Lindsley",
    subtitle = "",
    caption = "Data: PennPraxis, Metro Nashville")+
  mapTheme
```
- Broader context maps (e.g. whole city with venues and some basemap stuff?)

- Area maps for any geographic focus (e.g. North Nashville)